---
title: "Table1"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warnings = FALSE,
                      message = FALSE,
                      comment = "#>",
                      #results = "hide",
                      digits = 4,
                      error = FALSE)

## clean the R environment
graphics.off()
rm(list = ls())
freshr::freshr()

## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(gtsummary, quietly = TRUE)
library(flextable, quietly = TRUE)

## check the directory for the file
# here::dr_here()
here::set_here()

## the figure or results should be saved 
# paste0("foldername/Sfilename_workingresult_", 
#      Sys.Date(), ".filetype")
```

```{css, echo=FALSE}
.scroll-100 {
  max-height: 300px;
  max-width: 1000px;
  overflow-y: auto;
  background-color: inherit;
}
```

## Goal for this chapter

-   [x] Loading and Checking the data (has been cleaned by EJC removing all the id with NA)

-   [x] Data Cleaning (further cleaning, save into package internal `sysdata.rda`)

-   [x] Writing the data description, and save it in the `R` folder

-   [x] Entire data cleaning process is saved in the `data-raw` folder

-   [x] Building Table1 (Specifically looking at the `site` variable)

-   [x] Styling Table1 (using `gtsummary` package)

-   [x] Saving Table1 (as a `.tex` file)

## Data Cleaning

The data cleaning process codes are saved in the `data-raw` folder `swan_amh.R` file. The data cleaning process is done in the for both numeric `swan_amh0` and categorical `swan_amh1` data files. The data description is saved in the `R` folder as `00_data` files.

The cleaned data `.rda` is saved in the `data` folder as a part of the package which do not need to extra loading, if installed as a package. The extra copy of `.csv` files are saved in the `data-raw` folder for the reference.

```{r "loading_data"}
load(here("data", "swan_amh1.rda"))
```

Here is the final clean dataset `swan_amh1` with 600 individuals and 16 variables.

```{r, class.output="scroll-100"}
#| label: "swan_amh1"
swan_amh1
```

## Building Table1

```{r}
#| label: "create_table1"

table1 <- swan_amh1 %>%
  ungroup() %>%
  mutate(children = as.numeric(children),
         parity = case_when(parity == 0 ~ "None",
                            parity == 1 ~ "One",
                            parity == 2 ~ "Two",
                            parity == 3 ~ "Three",
                            parity == 4 ~ "More than three"),
         parity = factor(parity, levels = c("None", "One",
                                               "Two", "Three",
                                               "More than three"))) %>%
  dplyr::select(age, ethnic, married,
                alcohol, smoke, bc_pills,
                bmi, health, phys_act, amh,
                parity, children, 
                employed, edu, site)  %>%
  tbl_summary(by = site,
              missing = "ifany",
              label = list(c("age") ~ "Age (years)",
                           c("ethnic") ~ "Ethnicity / Race",
                           c("married") ~ "Marital Status",
                           c("alcohol") ~ "Alcohol Use",
                           c("smoke") ~ "Smoking History",
                           c("bc_pills") ~ "Ever use of BC Pills",
                           c("bmi") ~ "BMI",
                           c("health") ~ "Overall Health",
                           c("phys_act") ~ "Physical Activity Score",
                           c("amh") ~ "AMH",
                           c("parity") ~ "Parity",
                           c("children") ~ "Children",
                           c("employed") ~ "Employment Status",
                           c("edu") ~ "Educational Attainment"),
              type = list(all_continuous() ~ "continuous2",
                          c("children") ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                                    "{median}",
                                                    "[{min}, {max}]"),
                               all_categorical() ~ "{n} / {N} ({p}%)")) %>%
  modify_header(label = "**Characteristics**") %>%
  # update the column header
  bold_labels() %>%
  # add_overall() %>%
  italicize_labels()
```

Current Table1 is created, grouped by the `site` variable.

Need to be changed and updated with future requirements.

```{r  class.output="scroll-100"}
#| label: "styled_table1"
#| tbl-cap: "Descriptive Statistics for SWAN AMH Data"
set_flextable_defaults(font.size = 8, 
                       # text.align = "left",
                       theme_fun = theme_zebra,
                       padding = 2)
table1 %>% 
  as_flex_table() %>%
  fontsize(i = 1, size = 8, part = "header")
  
```

## Saving Table1

```{r "table_latex"}
#| label: "table_latex"
#| eval: false
library(xtable)
xtable(as.data.frame(table1), type = "latex",
      file = paste0("figure/swan_amh_01_table1_", Sys.Date(), ".tex"))
```

## Notes

The only problem is the location Sites with the Ethnicity groups.

Missing values are removed from 631 to 600 through data cleaning process.

See `data-raw/swan_amh.R` for the data cleaning process *`line-375` removed 31 individuals 31/631 = 4.9%*.
