---
title: "02_joint_model"
---

## BIOS6646. L14 Joint Models of Longitudinal and Survival Data"

`{ = tex} \newcommand{\bi}{\begin{itemize}} \newcommand{\ei}{\end{itemize}} \newcommand{\itt}{\item}`

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warnings = FALSE,
                      message = FALSE,
                      comment = "#>",
                      #results = "hide",
                      digits = 4,
                      error = FALSE)

## clean the R environment
graphics.off()
rm(list = ls())
freshr::freshr()

## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(gtsummary, quietly = TRUE)
library(flextable, quietly = TRUE)
library(JM)

## check the directory for the file
# here::dr_here()
here::set_here()

## the figure or results should be saved 
# paste0("foldername/Sfilename_workingresult_", 
#      Sys.Date(), ".filetype")
```

```{css, echo = FALSE}
.scroll-100 {
  max-height: 300px;
  max-width: 1000px;
  overflow-y: auto;
  background-color: inherit;
}
```

# In the JM package methods are available for the majority of the generic functions

-   summary(), anova(), vcov(), logLik(), AIC()
-   coef(),fixef(),ranef()
-   fitted(), residuals()
-   plot()

## Primary Biliary Cirrhosis (PBC) study

-   Primary biliary cirrhosis (PBC) is a chronic liver disease that leads to cirrhosis and eventually death

-   10-year study conducted by Mayo clinic (Murtagh et al., Hepatology, 1994)

-   158 randomized to treatment, 154 to placebo

-   Longitudinal biomarker measurements of serum bilirubin at times 0, 6m, 1y, 2y, etc.

\medskip

**Outcomes:**

1.  Longitudinal biomarker: serum bilirubin

2.  Time to death

**Question of interest:**

-   What is the association between the time-varying serum bilirubin (that is measured with error) and the risk of death?

```{r, "pbc_data", class.output = "scroll-100"}
pbc2
```

## Joint model

```{r "jm", eval = T, echo = T, include = T, out.width = "90%"}

lme.fit <- lme(log(serBilir) ~ year + year:drug, 
              data = pbc2, 
              random = ~year|id)

surv.fit <- coxph(Surv(years, status2) ~ drug, 
              data = pbc2.id, 
              x = TRUE)

## the knots of the piecewise constant are chosen based 
## on the percentiles of events 
## (5-6 internal knots by default)
joint.fit <- jointModel(lme.fit, surv.fit, 
              timeVar = "year", 
              method = "piecewise-PH-GH")
 
```

## Summary

```{r "jm.sum", eval = T, echo = T, include = T, out.width = "50%"}
##summary(joint.fit)

plot(joint.fit)
```

## Confidence intervals

```{r "jm.ci", eval = T, echo = T, include = T, out.width = "90%"}
confint(joint.fit, parm = 'all')
```

## AUC

```{r "jm.auc"}
#| warning: false

auc <- JM::aucJM(joint.fit, 
             newdata = pbc2, 
             Tstart = 5,
             Dt = 2)

roc <- JM::rocJM(joint.fit,
             data = pbc2,
             dt = c(2, 4, 8), 
             idVar = "id")

```

## Comparison of nested models

```{r "jm.lrt"}
surv.fit2 <- coxph(Surv(years, status2) ~ 1,
                   data = pbc2.id, 
                   x = TRUE)

joint.fit2 <- jointModel(lme.fit,
                         surv.fit2,
                         timeVar = "year", 
                         method = "piecewise-PH-GH")

anova(joint.fit2, joint.fit)

```

There is no drug effect in the survival outcome (model fits about the same).

# More practice with joint models

Use the data *aids* from the JM package. Take a look at *?aids* for a description of the dataset.

A randomized clinical trial in which longitudinal and survival data was collected to compare the efficacy and safety of two antiretroviral drugs in treating patients who had failed/were intolerant of AZT therapy

-   Longitudinal marker: CD4 cell counts
-   Survival outcome: time to death
-   Research goal: How is CD4 cell counts associated with a person’s risk of death?
-   Lower CD4 cell counts are associated with increased risk of death

```{r, "aids.data", class.output = "scroll-100"}
head(aids, 2)
```

### Fit the joint model based on the fitted linear mixed and Cox models using the function jointModel()

Interpret the association between CD4 counts and the risk of death.

```{r}
table(pbc2$status)
pbc2$status2 <- as.numeric(pbc2$status !=  "alive")
table(pbc2$status2)
pbc2.id$status2 <- as.numeric(pbc2.id$status !=  "alive")
table(pbc2.id$status2)
```

## Fitting joint models

```{r}
## linear mixed model fit (longitudinal outcome)
lme.fit <- lme(log(serBilir) ~ ns(year, 2),
               data = pbc2, 
               random = ~ns(year, 2)|id)
summary(lme.fit)

## cox model fit (survival outcome) with left truncation (need to fit model without left truncation)
surv.fit <- coxph(Surv(years, status2) ~ drug*age,
                  data = pbc2.id,
                  x = TRUE)
##surv.fit <- coxph(Surv(fmp.age, event) ~ menopause, data = dat1i, x = TRUE)
summary(surv.fit)
##plot(surv.fit)

## joint model fit
joint.fit <- jointModel(lme.fit, surv.fit, 
                        timeVar  = "year", 
                        method = "piecewise-PH-aGH")
summary(joint.fit)
##"weibull-PH-aGH"
##joint.fit.wei <- jointModel(lme.fit, surv.fit, timeVar  = "year", method = "weibull-PH-aGH")
##summary(joint.fit.wei)
```

## Obtaining dynamic predictions

```{r}
ids <- unique(pbc2$id)
## Prediction for the survival outcomes
ND1 <- pbc2[pbc2$id == ids[3], ]
sfit <- survfitJM(joint.fit,
                  newdata = ND1, 
                  idVar = "id") 
## do the covariates for survival model need to be in the long data?

quartz()
par(mfrow = c(1,1))
plot(sfit, estimator = "mean",
     include.y = TRUE,
     conf.int = TRUE, 
     fill.area = TRUE, 
     col.area = "lightgrey")


auc1 <- aucJM(joint.fit, 
              newdata = pbc2,
              idVar = "id", 
              Tstart = 5,
              Dt = 2) ## 
auc1
warnings()


auc2 <- aucJM(joint.fit,
              newdata = pbc2, 
              idVar = "id", 
              Tstart = 5, 
              Thoriz = 7) ## 
auc2
```
