---
title: "Table1 (for publication)"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      eval = TRUE,
                      warnings = FALSE,
                      message = FALSE,
                      comment = "#>",
                      cache = TRUE,
                      #results = "hide",
                      digits = 4,
                      error = FALSE)

## clean the R environment
# graphics.off()
# rm(list = ls())
# freshr::freshr()

## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(gtsummary, quietly = TRUE)
library(flextable, quietly = TRUE)
library(broom.mixed)
library(nlme)
library(JMbayes2)
devtools::load_all()

## check the directory for the file
# here::dr_here()
here::set_here()

## the figure or results should be saved 
# paste0("foldername/Sfilename_workingresult_", 
#      Sys.Date(), ".filetype")
```

\newpage

## To-do-list

- [x] run table 1 for the total sample size as 1 group

  - [x] Keeping table1 for one group (n = 600)

  - [x] Baseline levels of AMH (untransformed)
  
  - [X] also include the min and max of AMH

  - [x] How many repeated measures per woman

- [x] all the survival parameters summary 

- [x] all the longitudinal parameters summary

- [x] joint model summary

  - [x] with rate 
  
  - [x] without rate


\newpage

## Table1: descriptive summaries

Here is the Table1 for publication.

```{r "loading_data"}
load(here("data", "swan_amh1.rda"))
load(here("data", "swan_amh0.rda"))

sum_amh0 <- swan_amh0 %>%
  group_by(id) %>%
  summarize(visit_n = n(),
            amh_min = min(amh),
            amh_max = max(amh)) %>%
  ungroup() %>%
  mutate(id = as.character(id),
         visit_n = as.numeric(visit_n))

swan_amh2 <- swan_amh1 %>%
  full_join(sum_amh0, by = "id") %>%
  mutate(id = as.character(id),
         visit_n = as.numeric(visit_n))

```



```{r}
#| label: "create_table1"

table1 <- swan_amh2 %>%
  ungroup() %>%
  mutate(children = as.numeric(children),
         parity = case_when(parity == 0 ~ "None",
                            parity == 1 ~ "One",
                            parity == 2 ~ "Two",
                            parity == 3 ~ "Three",
                            parity == 4 ~ "More than three"),
         parity = factor(parity, levels = c("None", "One",
                                               "Two", "Three",
                                               "More than three"))) %>%
  dplyr::select(age, ethnic, married,
                alcohol, smoke, bc_pills,
                bmi, health, phys_act, amh,
                visit_n, # visit,
                parity, children, 
                employed, edu, site)  %>%
  tbl_summary(# by = site,
              missing = "ifany",
              label = list(c("age") ~ "Age (years)",
                           c("ethnic") ~ "Ethnicity / Race",
                           c("married") ~ "Marital Status",
                           c("alcohol") ~ "Alcohol Use",
                           c("smoke") ~ "Smoking History",
                           c("bc_pills") ~ "Ever use of BC Pills",
                           c("bmi") ~ "BMI",
                           c("health") ~ "Overall Health",
                           c("phys_act") ~ "Physical Activity Score",
                           c("amh") ~ "Baseline AMH",
                           c("parity") ~ "Parity",
                           c("children") ~ "Children",
                           c("employed") ~ "Employment Status",
                           c("edu") ~ "Educational Attainment",
                           c("visit_n") ~ "Number of Visits",
                           c("site") ~ "Site"),
              type = list(all_continuous() ~ "continuous2",
                          c("children", "visit_n") ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                                    "{median} [{min}, {max}]"),
                               all_categorical() ~ "{n} / {N} ({p}%)")) %>%
  modify_header(label = "**Characteristics**") %>%
  # update the column header
  bold_labels() %>%
  # add_overall() %>%
  italicize_labels()
```



```{r}
#| label: "styled_table1"
#| tbl-cap: "Descriptive Statistics for SWAN AMH Data"
#| warning: false

set_flextable_defaults(fonts_ignore=TRUE)
# set_flextable_defaults(font.size = 8, 
#                        # text.align = "left",
#                        # theme_fun = theme_zebra,
#                        padding = 2)
table1 %>% 
  as_flex_table() %>%
  fontsize(size = 8)
  
```

Here is the LaTeX code for the table1.

```{r "table1_latex"}
#| label: "table_latex"
#| eval: false
library(xtable)
xtable(as.data.frame(table1), type = "latex",
      file = paste0("figure/swan_amh_09_publish_table1_", Sys.Date(), ".tex"))
```


```
% latex table generated in R 4.2.2 by xtable 1.8-4 package
% Tue Apr  9 11:44:18 2024
\begin{table}[ht]
\centering
\begin{tabular}{rll}
  \hline
 & **Characteristics** & **N = 600** \\ 
  \hline
1 & \_\_\_Age (years)\_\_\_ &  \\ 
  2 & Mean (SD) & 46.42 (2.41) \\ 
  3 & Median & 46.00 \\ 
  4 & [Range] & [42.00, 53.00] \\ 
  5 & \_\_\_Ethnicity / Race\_\_\_ &  \\ 
  6 & CAUCA & 265 / 600 (44\%) \\ 
  7 & BLACK & 170 / 600 (28\%) \\ 
  8 & CHINE & 62 / 600 (10\%) \\ 
  9 & HISPA & 18 / 600 (3.0\%) \\ 
  10 & JAPAN & 85 / 600 (14\%) \\ 
  11 & \_\_\_Marital Status\_\_\_ &  \\ 
  12 & Not Married/Partnered & 191 / 600 (32\%) \\ 
  13 & Married/Partnered & 409 / 600 (68\%) \\ 
  14 & \_\_\_Alcohol Use\_\_\_ &  \\ 
  15 & None & 308 / 600 (51\%) \\ 
  16 & $<$1/wk & 71 / 600 (12\%) \\ 
  17 & 1-7/wk & 161 / 600 (27\%) \\ 
  18 & $>$7/wk & 60 / 600 (10\%) \\ 
  19 & \_\_\_Smoking History\_\_\_ &  \\ 
  20 & Never Smoked & 373 / 600 (62\%) \\ 
  21 & Past Only & 149 / 600 (25\%) \\ 
  22 & Current Smoker & 78 / 600 (13\%) \\ 
  23 & \_\_\_Ever use of BC Pills\_\_\_ &  \\ 
  24 & Never & 155 / 600 (26\%) \\ 
  25 & Ever use BC pills & 445 / 600 (74\%) \\ 
  26 & \_\_\_BMI\_\_\_ &  \\ 
  27 & Mean (SD) & 28 (7) \\ 
  28 & Median & 26 \\ 
  29 & [Range] & [16, 56] \\ 
  30 & \_\_\_Overall Health\_\_\_ &  \\ 
  31 & Excellent & 147 / 600 (25\%) \\ 
  32 & Very Good & 233 / 600 (39\%) \\ 
  33 & Good & 151 / 600 (25\%) \\ 
  34 & Fair/Poor & 69 / 600 (12\%) \\ 
  35 & \_\_\_Physical Activity Score\_\_\_ &  \\ 
  36 & Mean (SD) & 7.75 (1.77) \\ 
  37 & Median & 7.60 \\ 
  38 & [Range] & [3.40, 12.80] \\ 
  39 & \_\_\_Baseline AMH\_\_\_ &  \\ 
  40 & Mean (SD) & 540 (702) \\ 
  41 & Median & 273 \\ 
  42 & [Range] & [1, 4,652] \\ 
  43 & \_\_\_Number of Visits\_\_\_ &  \\ 
  44 & Mean (SD) & 5.54 (2.14) \\ 
  45 & Median & 5.00 \\ 
  46 & [Range] & [3.00, 11.00] \\ 
  47 & \_\_\_Parity\_\_\_ &  \\ 
  48 & None & 111 / 600 (19\%) \\ 
  49 & One & 88 / 600 (15\%) \\ 
  50 & Two & 210 / 600 (35\%) \\ 
  51 & Three & 116 / 600 (19\%) \\ 
  52 & More than three & 75 / 600 (13\%) \\ 
  53 & \_\_\_Children\_\_\_ &  \\ 
  54 & Mean (SD) & 1.98 (1.41) \\ 
  55 & Median & 2.00 \\ 
  56 & [Range] & [0.00, 12.00] \\ 
  57 & \_\_\_Employment Status\_\_\_ &  \\ 
  58 & Unemployed & 104 / 600 (17\%) \\ 
  59 & Employed & 496 / 600 (83\%) \\ 
  60 & \_\_\_Educational Attainment\_\_\_ &  \\ 
  61 & High School or Less & 125 / 600 (21\%) \\ 
  62 & Some College & 190 / 600 (32\%) \\ 
  63 & College degree or higher & 285 / 600 (48\%) \\ 
  64 & \_\_\_Site\_\_\_ &  \\ 
  65 & B & 96 / 600 (16\%) \\ 
  66 & C & 76 / 600 (13\%) \\ 
  67 & M & 103 / 600 (17\%) \\ 
  68 & NJ & 27 / 600 (4.5\%) \\ 
  69 & P & 74 / 600 (12\%) \\ 
  70 & UCD & 102 / 600 (17\%) \\ 
  71 & UCLA & 122 / 600 (20\%) \\ 
   \hline
\end{tabular}
\end{table}
```

\newpage


## Table2: summary for AMH and visits

```{r}
#| label: "create_table2"
table2 <- swan_amh2 %>%
  ungroup() %>%
  dplyr::select(amh,
                amh_min,
                amh_max,
                visit_n)  %>%
  tbl_summary(# by = site,
              missing = "ifany",
              label = list(c("amh") ~ "Baseline AMH",
                           c("amh_min") ~ "Minimum AMH",
                           c("amh_max") ~ "Maximum AMH",
                           c("visit_n") ~ "Number of Visits"),
              type = list(all_continuous() ~ "continuous2",
                          c("visit_n") ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                                    "{median} [{p25}, {p75}]",
                                                    "{median} [{p5}, {p95}]",
                                                    "{median} [{min}, {max}]"))) %>%
  modify_header(label = "**Characteristics**") %>%
  # update the column header
  bold_labels() %>%
  # add_overall() %>%
  italicize_labels()
```

```{r}
#| label: "styled_table2"
#| tbl-cap: "Descriptive Statistics for SWAN AMH Data"

set_flextable_defaults(fonts_ignore=TRUE)

table2 %>% 
  as_flex_table() %>%
  fontsize(size = 8)
  
```


```{r "table2_latex"}
#| label: "table2_latex"
#| eval: false
library(xtable)
xtable(as.data.frame(table2), type = "latex",
      file = paste0("figure/swan_amh_09_publish_table2_", Sys.Date(), ".tex"))
```

Here is the latex code for Table2:

```
% latex table generated in R 4.2.2 by xtable 1.8-4 package
% Tue Apr  9 14:00:42 2024
\begin{table}[ht]
\centering
\begin{tabular}{rll}
  \hline
 & **Characteristics** & **N = 600** \\ 
  \hline
1 & \_\_\_Baseline AMH\_\_\_ &  \\ 
  2 & Mean (SD) & 540 (702) \\ 
  3 & Median [IQR] & 273 [71, 672] \\ 
  4 & Median [5\%, 95\%] & 273 [1, 2,095] \\ 
  5 & Median [Range] & 273 [1, 4,652] \\ 
  6 & \_\_\_Minimum AMH\_\_\_ &  \\ 
  7 & Mean (SD) & 28 (78) \\ 
  8 & Median [IQR] & 2 [1, 18] \\ 
  9 & Median [5\%, 95\%] & 2 [1, 133] \\ 
  10 & Median [Range] & 2 [1, 772] \\ 
  11 & \_\_\_Maximum AMH\_\_\_ &  \\ 
  12 & Mean (SD) & 628 (730) \\ 
  13 & Median [IQR] & 341 [132, 836] \\ 
  14 & Median [5\%, 95\%] & 341 [23, 2,174] \\ 
  15 & Median [Range] & 341 [1, 4,681] \\ 
  16 & \_\_\_Number of Visits\_\_\_ &  \\ 
  17 & Mean (SD) & 5.54 (2.14) \\ 
  18 & Median [IQR] & 5.00 [4.00, 7.00] \\ 
  19 & Median [5\%, 95\%] & 5.00 [3.00, 10.00] \\ 
  20 & Median [Range] & 5.00 [3.00, 11.00] \\ 
   \hline
\end{tabular}
\end{table}
```

\newpage

## Longitudinal model 

$lme.fit1: \ \ \  (fixed = lamh \sim time, \ random = \sim time| id)$

Here is the summary for longitudinal sub-model, based on model selection

```{r}
#| label: "dummy_variables"
swan_amh12 <- swan_amh11 %>%
  cbind(model.matrix(~ 0 + site_ethnic + smoke, 
                                    data = .)) %>%
  janitor::clean_names() %>% 
  dplyr::select(order(colnames(.)))

swan_amh02 <- swan_amh00 %>%
  mutate(smoke = case_when(smoke == 1 ~ "Past Only",
                           smoke == 2 ~ "Current Smoker",
                           smoke == 3 ~ "Never Smoked"),
         smoke = factor(smoke, levels = c("Never Smoked" , "Past Only", "Current Smoker"))) %>%
  cbind(model.matrix(~ 0 + site_ethnic + smoke, 
                                    data = .)) %>%
  janitor::clean_names() %>% 
  dplyr::select(order(colnames(.)))


control = lmeControl(opt = "optim")
lme.fit1 <- lme(lamh ~ time,
                data = swan_amh00,
                control = control,
                random = ~ time| id)
```

Here is the table for the longitudinal model:

```{r}
broom.mixed::tidy(lme.fit1) %>% knitr::kable()
```

The full summary for the longitudinal model is as follows:


```{r}
summary(lme.fit1)
```

\newpage

## Survival model 

**Notes: is it necessary to include a model with observed AMH as covariate in survival model?**

$surv.fit16: \ \ \  coxph(Surv(etime, event) \sim married + bc\_pills + bmi + factor(site) + factor(ethnic) + factor(smoke))$

Here is the table for survival model, based on model selection:

```{r}
#| label: "survival_model"
surv.fit16 <- coxph(Surv(etime, event) ~ 0 + married + bc_pills + bmi +
                      site_ethnic_b_black + # site_ethnic_b_cauca + 
                      site_ethnic_c_black + site_ethnic_c_cauca + 
                      site_ethnic_m_black + site_ethnic_m_cauca +
                      site_ethnic_nj_cauca + site_ethnic_nj_hispa +
                      site_ethnic_p_black + site_ethnic_p_cauca + 
                      site_ethnic_ucd_cauca + site_ethnic_ucd_chine +
                      site_ethnic_ucla_cauca + site_ethnic_ucla_japan +
                      smoke_past_only + smoke_current_smoker,
                    data = swan_amh12, 
                    x = TRUE,
                    model = TRUE)
```


```{r}
broom::tidy(surv.fit16) %>% knitr::kable()

```

Here is the summary for the survival model

```{r}
summary(surv.fit16)

```

\newpage

## Joint model without Rate (only value term of longitudinal submodel)

$$
\begin{split}
  jmbayes2.fit116: & \\ 
  lme.fit1: \ \ \  & \pmb m(time) = (fixed = lamh \sim time, \ random = \sim time| id) \\
  surv.fit16: \ \ \ & Surv(etime, event) \sim married + bc\_pills + bmi + factor(site) + \\
  & factor(ethnic) + factor(smoke) + \pmb m(time)
\end{split}
$$

### Longitudinal submodel

```{r}
#| label: "joint_model_no_rate"
jmcontrol <- list(n_iter = 5000, 
                  n_burnin = 1000, 
                  n_chains = 1,
                  seed = 55555,
                  cores = 1)

jmbayes2.fit116 <- JMbayes2::jm(Surv_object = surv.fit16,
                               Mixed_objects = lme.fit1, 
                               time_var = "time",
                               control = jmcontrol) 
```

Here is the summary for longitudinal submodel:

```{r}
summary(jmbayes2.fit116)$Outcome1 %>% knitr::kable()
```

### Survival submodel

Here is the summary for survival submodel:

```{r}
summary(jmbayes2.fit116)$Survival %>% knitr::kable()
```

### Joint model

Here are the full summary for the joint model without rate:

```{r}
summary(jmbayes2.fit116)

```

\newpage

## Joint model with rate (value and rate terms of longitudinal submodel)

$$
\begin{split}
  jmbayes2.fit116.d: & \\
  lme.fit1: \ \ \  & \pmb m(time) = (fixed = lamh \sim time, \ random = \sim time| id) \\
  surv.fit16: \ \ \ & Surv(etime, event) \sim married + bc\_pills + bmi + \\
  & factor(site) + factor(ethnic) + factor(smoke) + \pmb m(time) + \pmb m'(time)
\end{split}
$$

```{r}
jmbayes2.fit116.d <- JMbayes2::jm(Surv_object = surv.fit16,
                                  Mixed_objects = lme.fit1, 
                                  functional_forms = list("lamh" = ~ value(lamh) + slope(lamh)),
                                  time_var = "time",
                                  control = jmcontrol,
                                  seed = 55555) 
                         
```

### Longitudinal submodel

Here is the summary for longitudinal submodel:

```{r}
summary(jmbayes2.fit116.d)$Outcome1 %>% knitr::kable()
```

### Survival submodel

Here is the summary for survival submodel:

```{r}
summary(jmbayes2.fit116.d)$Survival %>% knitr::kable()
```

### Joint model

Here are the full summary for the joint model with rate:

```{r}
summary(jmbayes2.fit116.d)
```

\newpage

## Comparison for model with and without rate

```{r}
#| label: "compare_jmbayes2"

compare_jm(jmbayes2.fit116.d, jmbayes2.fit116)
```








