---
title: "Final model (for publication)"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warnings = FALSE,
                      message = FALSE,
                      comment = "#>",
                      cache = TRUE,
                      #results = "hide",
                      digits = 4,
                      error = FALSE)

# ## clean the R environment
# graphics.off()
# rm(list = ls())
# freshr::freshr()

## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(JMbayes2, quietly = TRUE)
devtools::load_all()

## check the directory for the file
# here::dr_here()
here::set_here()

## the figure or results should be saved 
# paste0("foldername/Sfilename_workingresult_", 
#      Sys.Date(), ".filetype")
```

```{css, "css-setup", echo=FALSE}
.scroll-100 {
  max-height: 300px;
  max-width: 1000px;
  overflow-y: auto;
  background-color: inherit;
}
```

## Goal of the analysis

-   [x] To separate the `site` and `ethnicity` as dummy variables

-   [x] Fit the final joint model (without rate) with `JMbayes2` based on model selection results

-   [x] Dynamic prediction for the joint model with plots

-   [x] Calculate the AUC and ROC for the joint model for $Dt = 1, 2, 3, 4, 5$ (year)

## Dummy variables for `site` and `ethnicity`

```{r}
#| label: "dummy_variables"
swan_amh13 <- swan_amh1 %>%
  cbind(model.matrix(~ 1 + site + ethnic + smoke, 
                                    data = .)) %>%
  mutate(ethnic = factor(ethnic, levels = c("CAUCA", "BLACK", 
                                            "CHINE", "HISPA", 
                                            "JAPAN"))) %>%
  janitor::clean_names() %>% 
  dplyr::select(-intercept) %>%
  dplyr::select(order(colnames(.)))

swan_amh03 <- swan_amh0 %>%
  mutate(smoke = case_when(smoke == 1 ~ "Past Only",
                           smoke == 2 ~ "Current Smoker",
                           smoke == 3 ~ "Never Smoked"),
         site = case_when(site == "11" ~ "M",
                          site == "12" ~ "B",
                          site =="13" ~ "C",
                          site =="14" ~ "UCD",
                          site =="15" ~ "UCLA",
                          site =="16" ~ "NJ",
                          site =="17" ~ "P"),
         ethnic = factor(ethnic, levels = c("CAUCA", "BLACK", 
                                            "CHINE", "HISPA", 
                                            "JAPAN")),
         site = factor(site, levels = c("B", "C", "M", 
                                        "NJ", "P", 
                                        "UCD", "UCLA")),
         smoke = factor(smoke, levels = c("Never Smoked" , 
                                          "Past Only", 
                                          "Current Smoker"))) %>%
  cbind(model.matrix(~ 1 + site + ethnic + smoke, 
                     data = .)) %>%
  janitor::clean_names() %>% 
  dplyr::select(-intercept) %>%
  dplyr::select(order(colnames(.)))

# names(swan_amh13)
# names(swan_amh03)
# View(swan_amh03)
# View(swan_amh13)

# levels(swan_amh13$ethnic)
## CAUCAsion is the reference group
## **"CAUCA"** "BLACK" "CHINE" "HISPA" "JAPAN"

# table(swan_amh13$site)
## B is the reference group
##   **"B"**  "C"  "M"  "NJ"  "P"  "UCD"  "UCLA" 

# levels(swan_amh13$smoke) 
## NeverSmoked is the reference group
## "Never Smoked" "Past Only" "Current Smoker"

# ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
# site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
# smoke_current_smoker + smoke_past_only

```

## Fit the joint model

### Longitudinal model

$lme1: \ \ \  (fixed = lamh \sim time, \ random = \sim time| id)$

Summary for the longitudinal model:

```{r}
#| label: " longitudinal"
control = lmeControl(opt = "optim")
lme1 <- lme(lamh ~ time,
                data = swan_amh00,
                control = control,
                random = ~ time| id)

broom.mixed::tidy(lme1) %>% knitr::kable()

# xtable::xtable(broom.mixed::tidy(lme1), caption = "Longitudinal model")
```

Here is the latex code for the longitudinal model:

```{tex}
% latex table generated in R 4.2.2 by xtable 1.8-4 package
% Wed Apr 10 20:46:26 2024
\begin{table}[ht]
\centering
\begin{tabular}{rlllrrrrr}
  \hline
 & effect & group & term & estimate & std.error & df & statistic & p.value \\ 
  \hline
1 & fixed &  & (Intercept) & 7.52 & 0.10 & 2725.00 & 72.11 & 0.00 \\ 
  2 & fixed &  & time & -0.53 & 0.01 & 2725.00 & -45.64 & 0.00 \\ 
  3 & ran\_pars & id & sd\_(Intercept) & 1.68 &  &  &  &  \\ 
  4 & ran\_pars & id & cor\_time.(Intercept) & -0.36 &  &  &  &  \\ 
  5 & ran\_pars & id & sd\_time & 0.10 &  &  &  &  \\ 
  6 & ran\_pars & Residual & sd\_Observation & 1.30 &  &  &  &  \\ 
   \hline
\end{tabular}
\caption{Longitudinal model} 
\end{table}

```

### Survival model

$surv16: \ \ \  coxph(Surv(etime, event) \sim married + bc\_pills + bmi + factor(site) + factor(ethnic) + factor(smoke))$

Summary for the survival model:

```{r}
#| label: "survival"
## testing for health
## site_ethnic_b_cauca as the reference group 
surv16 <- coxph(Surv(etime, event) ~ 0 + married + bc_pills + bmi +
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13, 
                x = TRUE,
                model = TRUE)

broom.mixed::tidy(surv16) %>% knitr::kable()

# xtable::xtable(broom.mixed::tidy(surv16), caption = "Survival model")

```

Here is the latex code for the survival model:

```{tex}
% latex table generated in R 4.2.2 by xtable 1.8-4 package
% Wed Apr 10 20:49:12 2024
\begin{table}[ht]
\centering
\begin{tabular}{rlrrrr}
  \hline
 & term & estimate & std.error & statistic & p.value \\ 
  \hline
1 & marriedMarried/Partnered & 0.22 & 0.09 & 2.30 & 0.02 \\ 
  2 & bc\_pillsEver use BC pills & -0.23 & 0.10 & -2.29 & 0.02 \\ 
  3 & bmi & -0.00 & 0.01 & -0.46 & 0.65 \\ 
  4 & ethnic\_black & -0.18 & 0.12 & -1.51 & 0.13 \\ 
  5 & ethnic\_chine & -0.05 & 0.21 & -0.22 & 0.82 \\ 
  6 & ethnic\_hispa & -0.20 & 0.41 & -0.49 & 0.62 \\ 
  7 & ethnic\_japan & -0.18 & 0.20 & -0.88 & 0.38 \\ 
  8 & site\_c & 0.11 & 0.16 & 0.69 & 0.49 \\ 
  9 & site\_m & 0.27 & 0.15 & 1.77 & 0.08 \\ 
  10 & site\_nj & 0.20 & 0.35 & 0.56 & 0.58 \\ 
  11 & site\_p & 0.57 & 0.16 & 3.53 & 0.00 \\ 
  12 & site\_ucd & 0.23 & 0.20 & 1.17 & 0.24 \\ 
  13 & site\_ucla & 0.26 & 0.21 & 1.28 & 0.20 \\ 
  14 & smoke\_current\_smoker & 0.59 & 0.14 & 4.36 & 0.00 \\ 
  15 & smoke\_past\_only & 0.07 & 0.10 & 0.65 & 0.51 \\ 
   \hline
\end{tabular}
\caption{Survival model} 
\end{table}
```

### Joint model

$$
\begin{split}
  jmbayes2.116: & \\ 
  lme1: \ \ \  & \pmb m(time) = (fixed = lamh \sim time, \ random = \sim time| id) \\
  surv16: \ \ \ & Surv(etime, event) \sim married + bc\_pills + bmi + factor(site) + \\
  & factor(ethnic) + factor(smoke) + \pmb m(time)
\end{split}
$$

```{r}
#| label: "joint_model"
jmcontrol <- list(n_iter = 5000, 
                  n_burnin = 1000, 
                  n_chains = 3,
                  seed = 55555,
                  cores = 3)

jmbayes2.116 <- JMbayes2::jm(Surv_object = surv16,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

# save(jmbayes2.116, file = here::here("results", "jmbayes2.116.RData"))
```

For the `lme` sub-model:

```{r}
#| label: "lme_summary"
summary(jmbayes2.116)$Outcome1 %>% knitr::kable()
# xtable::xtable(summary(jmbayes2.116)$Outcome1, caption = "Longitudinal model")
```

```{tex}
% latex table generated in R 4.2.2 by xtable 1.8-4 package
% Wed Apr 10 21:31:42 2024
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrr}
  \hline
 & Mean & StDev & 2.5\% & 97.5\% & P & Rhat \\ 
  \hline
(Intercept) & 7.91 & 0.11 & 7.71 & 8.13 & 0.00 & 1.01 \\ 
  time & -0.60 & 0.01 & -0.62 & -0.57 & 0.00 & 1.02 \\ 
  sigma & 1.31 & 0.02 & 1.27 & 1.34 & 0.00 & 1.00 \\ 
   \hline
\end{tabular}
\caption{Longitudinal model} 
\end{table}
```

For the `surv` sub-model:

```{r}
#| label: "survival_summary"
summary(jmbayes2.116)$Survival %>% knitr::kable()
# xtable::xtable(summary(jmbayes2.116)$Survival, caption = "Survival model")
```


```{tex}
% latex table generated in R 4.2.2 by xtable 1.8-4 package
% Wed Apr 10 21:30:38 2024
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrr}
  \hline
 & Mean & StDev & 2.5\% & 97.5\% & P & Rhat \\ 
  \hline
marriedMarried/Partnered & 0.13 & 0.15 & -0.16 & 0.41 & 0.39 & 1.01 \\ 
  bc\_pillsEver use BC pills & -0.03 & 0.13 & -0.29 & 0.24 & 0.82 & 1.00 \\ 
  bmi & -0.05 & 0.01 & -0.07 & -0.03 & 0.00 & 1.02 \\ 
  ethnic\_black & -0.37 & 0.15 & -0.66 & -0.07 & 0.01 & 1.00 \\ 
  ethnic\_chine & -0.23 & 0.28 & -0.75 & 0.33 & 0.41 & 1.01 \\ 
  ethnic\_hispa & -0.61 & 0.61 & -1.76 & 0.62 & 0.33 & 1.05 \\ 
  ethnic\_japan & -0.04 & 0.27 & -0.56 & 0.47 & 0.89 & 1.01 \\ 
  site\_c & 0.24 & 0.20 & -0.16 & 0.62 & 0.25 & 1.01 \\ 
  site\_m & 0.33 & 0.19 & -0.04 & 0.71 & 0.08 & 1.02 \\ 
  site\_nj & 0.64 & 0.49 & -0.35 & 1.57 & 0.21 & 1.02 \\ 
  site\_p & 0.51 & 0.20 & 0.13 & 0.92 & 0.01 & 1.02 \\ 
  site\_ucd & 0.14 & 0.26 & -0.38 & 0.64 & 0.57 & 1.02 \\ 
  site\_ucla & 0.42 & 0.26 & -0.09 & 0.95 & 0.10 & 1.02 \\ 
  smoke\_current\_smoker & 0.17 & 0.18 & -0.19 & 0.53 & 0.30 & 1.01 \\ 
  smoke\_past\_only & -0.07 & 0.13 & -0.33 & 0.20 & 0.60 & 1.00 \\ 
  value(lamh) & -1.01 & 0.07 & -1.15 & -0.88 & 0.00 & 1.06 \\ 
   \hline
\end{tabular}
\caption{Survival model} 
\end{table}
```

***Notice: ask EJC for which computer to use for long chain runing***

```{r}
#| label: "traceplots"
#| layout-nrow: 6
# par(mfrow = c(5, 7))
traceplot(jmbayes2.116)
```

## Dynamic prediction

### Individual prediction plots

```{r}
#| label: "ddplot_function"
ids <- unique(swan_amh03$id)
dpplot <- function(id_num,
                   tmin = 0,
                   tmax = 12,
                   jmfit = jmbayes2.116,
                   ...){

  # browser()
  # ids <- unique(swan_amh03$id)
  nid0 <- swan_amh03[swan_amh03$id == ids[id_num], ]
  
  nid <- nid0
  nid <- nid[nid$time < tmin, ]
  nid$event <- 0
  nid$etime <- tmin
  
  Lpred <- predict(jmfit, 
                    newdata = nid,
                   times = seq(tmin, tmax, length.out = 11),
                    return_newdata = TRUE)
  Spred <- predict(jmfit, 
                 newdata = nid,
                 times = seq(tmin, tmax, length.out = 11),
                 process = "event",
                 return_newdata = TRUE)
  
  plot(Lpred, Spred, 
       ylab_long = paste0("ID_", id_num, "  log(amh)"))
  
  return(list(Lpred = Lpred,
              Spred = Spred,
              nid0 = nid0,
              nid = nid))
}

```

```{r}
#| label: "dyn_plots_high"
#| layout-nrow: 3
dpplot_id5 <- map(c(4, 6, 8), 
               ~dpplot(id_num = 5,
                       tmin = .x, 
                       tmax = 12))

dpplot_id26 <- map(c(4, 6, 8), 
               ~dpplot(id_num = 26,
                       tmin = .x, 
                       tmax = 12))

dpplot_id333 <- map(c(4, 6, 8),
               ~dpplot(id_num = 342,
                       tmin = .x,
                       tmax = 12))
```


```{r}
#| label: "dyn_plots_low"
#| layout-nrow: 3
dpplot_id32 <- map(c(4, 6, 8), 
               ~try(dpplot(id_num = 57,
                       tmin = .x, 
                       tmax = 12)))

dpplot_id371 <- map(c(4, 6, 8), 
               ~try(dpplot(id_num = 371,
                       tmin = .x, 
                       tmax = 12)))

dpplot_id44 <- map(c(4, 6, 8),
               ~try(dpplot(id_num = 44,
                       tmin = .x,
                       tmax = 12)))
```

## AUC and ROC

For `JMbayes2`, the function `tvAUC()` is used to estimate the time-dependent AUC only for all the subjects (there is no function for individual AUC). Here is an error message for the AUC $Tstart = 2$ $Dt = 1$

```
Error in tvROC.jm(object, newdata, Tstart, Thoriz, Dt, ...) : 
  it seems that there are no events in the interval [Tstart, Thoriz).
```


```{r}
#| label: "auc_summary"

AUC2  <- map(c(1, 2, 3, 4, 5), 
                 ~try(JMbayes2::tvAUC(jmbayes2.116,
                                      swan_amh03,
                                      Tstart = 2,
                                      Dt = .x)))

AUC4  <- map(c(1, 2, 3, 4, 5), 
                 ~try(JMbayes2::tvAUC(jmbayes2.116,
                                      swan_amh03,
                                      Tstart = 4,
                                      Dt = .x)))

AUC6  <- map(c(1, 2, 3, 4, 5), 
                 ~try(JMbayes2::tvAUC(jmbayes2.116,
                                      swan_amh03,
                                      Tstart = 6,
                                      Dt = .x)))

AUC8  <- map(c(1, 2, 3, 4, 5), 
                 ~try(JMbayes2::tvAUC(jmbayes2.116,
                                      swan_amh03,
                                      Tstart = 8,
                                      Dt = .x)))
```


```{r}
#| label: "auc_table"
#| warning: false
Tstart2 = map(AUC2, "auc") %>% as.character()
Tstart4 = map(AUC4, "auc") %>% as.character()
Tstart6 = map(AUC6, "auc") %>% as.character()
Tstart8 = map(AUC8, "auc") %>% as.character()

tbl_auc <- rbind(Tstart2, Tstart4,
      Tstart6, Tstart8) %>% 
  as.data.frame() %>%
  mutate_all(as.numeric) %>%
  round(4)

names(tbl_auc) <- c("Dt1", "Dt2", "Dt3", "Dt4", "Dt5")

tbl_auc
```


The ROC curves for the joint model for $Tstart = 2, 4, 6, 8$ by rows,

and $Dt = 2, 3, 4, 5$ by columns are shown below:



```{r}
#| label: "roc_plots"
#| layout-nrow: 4

ROC2  <- map(c(2, 3, 4, 5), 
                 ~try(JMbayes2::tvROC(jmbayes2.116,
                                      swan_amh03,
                                      Tstart = 2,
                                      Dt = .x) %>% plot()) )

ROC4  <- map(c(2, 3, 4, 5), 
                 ~try(JMbayes2::tvROC(jmbayes2.116,
                                      swan_amh03,
                                      Tstart = 4,
                                      Dt = .x) %>% plot()))

ROC6  <- map(c(2, 3, 4, 5), 
                 ~try(JMbayes2::tvROC(jmbayes2.116,
                                      swan_amh03,
                                      Tstart = 6,
                                      Dt = .x) %>% plot()))

ROC8  <- map(c(2, 3, 4, 5), 
                 ~try(JMbayes2::tvROC(jmbayes2.116,
                                      swan_amh03,
                                      Tstart = 8,
                                      Dt = .x) %>% plot()))
```


## Brier Score

The warning massage for the Brier score is shown below:

```
Error in br(Thoriz) : 
  it seems that there are no events in the interval [2.000001, 3).

Warning: there are fewer than 5 subjects with an event in the interval [2.000001, 4).
```

```{r}
#| label: "bs_summary"

Brier2  <- map(c(1, 2, 3, 4, 5), 
                 ~try(JMbayes2::tvBrier(jmbayes2.116,
                                      swan_amh03,
                                      Tstart = 2,
                                      Dt = .x)))

Brier4  <- map(c(1, 2, 3, 4, 5), 
                 ~try(JMbayes2::tvBrier(jmbayes2.116,
                                      swan_amh03,
                                      Tstart = 4,
                                      Dt = .x)))

Brier6  <- map(c(1, 2, 3, 4, 5), 
                 ~try(JMbayes2::tvBrier(jmbayes2.116,
                                      swan_amh03,
                                      Tstart = 6,
                                      Dt = .x)))

Brier8  <- map(c(1, 2, 3, 4, 5), 
                 ~try(JMbayes2::tvBrier(jmbayes2.116,
                                      swan_amh03,
                                      Tstart = 8,
                                      Dt = .x)))
```


```{r}
#| label: "bs_table"
#| warning: false
Tstart2 = map(Brier2, "Brier") %>% as.character()
Tstart4 = map(Brier4, "Brier") %>% as.character()
Tstart6 = map(Brier6, "Brier") %>% as.character()
Tstart8 = map(Brier8, "Brier") %>% as.character()

tbl_auc <- rbind(Tstart2, Tstart4,
      Tstart6, Tstart8) %>% 
  as.data.frame() %>%
  mutate_all(as.numeric) %>%
  round(4)

names(tbl_auc) <- c("Dt1", "Dt2", "Dt3", "Dt4", "Dt5")

tbl_auc
```














