---
title: "Model Selection I - Dummy"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warnings = FALSE,
                      message = FALSE,
                      comment = "#>",
                      cache = TRUE,
                      #results = "hide",
                      digits = 4,
                      error = FALSE)

# ## clean the R environment
# graphics.off()
# rm(list = ls())
# freshr::freshr()

## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(plyr)
library(JMbayes2, quietly = TRUE)
devtools::load_all()

## check the directory for the file
# here::dr_here()
here::set_here()

```

```{css, "css-setup", echo=FALSE}
.scroll-100 {
  max-height: 300px;
  max-width: 1000px;
  overflow-y: auto;
  background-color: inherit;
}
```

## Goal of the analysis

-   [x] Backward model selection joint model (without rate) with `JMbayes2`

-   [x] Rate model, Baseline Rate model, Value model comparison

-   [x] Tables for the models

-   [x] `r praise::praise()`

## Dummy variables for `site` and `ethnicity`

```{r}
#| label: "dummy_variables"

load("data/swan_amh03.rda")
load("data/swan_amh13.rda")


control = lmeControl(opt = "optim")
jmcontrol <- list(n_iter = 5000, 
                  n_burnin = 1000, 
                  n_chains = 3,
                  seed = 55555,
                  cores = 3)
```

## Fit the joint model

Need to keep $site + ethnic + smoke + bmi$

### Full model

```{r}
lme1 <- lme(lamh ~ time,
                data = swan_amh03,
                control = control,
                random = ~ time| id)

## surv11 is the full model with all the variables
surv11 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + bc_pills + 
                  children + edu + employed +
                  health +
                  married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13, 
                x = TRUE,
                model = TRUE)

jmb2.111 <- JMbayes2::jm(Surv_object = surv11,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb2.111)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

### Dropping `alcohol < 1/wk` variable

```{r}
levels(swan_amh13$alcohol)
swan_amh13.12 <- swan_amh13 %>%
  transform(alcohol = revalue(alcohol,
                              c("<1/wk" = "None")))
levels(swan_amh13.12$alcohol)
remove(swan_amh13)

surv12 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + bc_pills + 
                  children + edu + employed +
                  health +
                  married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.12, 
                x = TRUE,
                model = TRUE)

jmb2.112 <- JMbayes2::jm(Surv_object = surv12,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb2.112)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

### Dropping The `edu College degree or higher` variable

```{r}
levels(swan_amh13.12$edu)
swan_amh13.13 <- swan_amh13.12 %>%
  transform(edu = revalue(edu,
                          c("College degree or higher" = "Some College")))
levels(swan_amh13.13$edu)
remove(swan_amh13.12)

surv13 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + bc_pills + 
                  children + edu + employed +
                  health +
                  married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.13, 
                x = TRUE,
                model = TRUE)

jmb2.113 <- JMbayes2::jm(Surv_object = surv13,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb2.113)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

### Dropping `health Good` variable

```{r}
levels(swan_amh13.13$health)
swan_amh13.14 <- swan_amh13.13 %>%
  transform(health = revalue(health,
                             c("Good" = "Excellent")))
levels(swan_amh13.14$health)
remove(swan_amh13.13)

surv14 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + bc_pills + 
                  children + edu + employed +
                  health +
                  married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.14, 
                x = TRUE,
                model = TRUE)

jmb2.114 <- JMbayes2::jm(Surv_object = surv14,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb2.114)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

### Dropping `health Fair/Poor` variable

```{r}
levels(swan_amh13.14$health)
swan_amh13.15 <- swan_amh13.14 %>%
  transform(health = revalue(health,
                             c("Fair/Poor" = "Excellent")))
levels(swan_amh13.15$health)
remove(swan_amh13.14)

surv15 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + bc_pills + 
                  children + edu + employed +
                  health +
                  married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.15, 
                x = TRUE,
                model = TRUE)

jmb2.115 <- JMbayes2::jm(Surv_object = surv15,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb2.115)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

### Dropping `alcohol >7/wk` variable

```{r}
levels(swan_amh13.15$alcohol)
swan_amh13.16 <- swan_amh13.15 %>%
  transform(alcohol = revalue(alcohol,
                              c(">7/wk" = "None")))
levels(swan_amh13.16$alcohol)
remove(swan_amh13.15)

surv16 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + bc_pills + 
                  children + edu + employed +
                  health +
                  married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.16, 
                x = TRUE,
                model = TRUE)

jmb2.116 <- JMbayes2::jm(Surv_object = surv16,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb2.116)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

### Dropping `bc_pills Ever use BC pills` variable

```{r}
levels(swan_amh13.16$bc_pills)
swan_amh13.17 <- swan_amh13.16

# swan_amh13.6 <- swan_amh13.5 %>%
#   transform(alcohol = revalue(alcohol,
#                               c(">7/wk" = "None")))
remove(swan_amh13.16)

surv17 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + 
                  # bc_pills + 
                  children + 
                  edu + 
                  employed +
                  health +
                  married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.17, 
                x = TRUE,
                model = TRUE)

jmb2.117 <- JMbayes2::jm(Surv_object = surv17,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb2.117)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

### Dropping `health Very Good` variable

```{r}
levels(swan_amh13.17$health)
swan_amh13.18 <- swan_amh13.17
remove(swan_amh13.17)

surv18 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi +  
                  # bc_pills + 
                  children + 
                  edu + employed +
                  # health +
                  married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.18, 
                x = TRUE,
                model = TRUE)

jmb2.118 <- JMbayes2::jm(Surv_object = surv18,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb2.118)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

### Dropping `employed Employed` variable

```{r}
levels(swan_amh13.18$employed)
swan_amh13.19 <- swan_amh13.18
remove(swan_amh13.18)

surv19 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + 
                  # bc_pills + 
                  children + 
                  edu + 
                  # employed +
                  # health +
                  married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.19, 
                x = TRUE,
                model = TRUE)

jmb2.119 <- JMbayes2::jm(Surv_object = surv19,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb2.119)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

### Dropping `children` variable

```{r}
table(swan_amh13.19$children)
swan_amh13.20 <- swan_amh13.19
remove(swan_amh13.19)

surv20 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + # bc_pills + 
                  # children +
                  edu + 
                  # employed +
                  # health +
                  married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.20, 
                x = TRUE,
                model = TRUE)

jmb2.120 <- JMbayes2::jm(Surv_object = surv20,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb2.120)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

### Dropping `married Married/Partnered` variable

```{r}
table(swan_amh13.20$married)
swan_amh13.21 <- swan_amh13.20
remove(swan_amh13.20)

surv21 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + # bc_pills + 
                  #children +
                  edu + 
                  # employed +
                  # health +
                  # married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.21, 
                x = TRUE,
                model = TRUE)

jmb2.121 <- JMbayes2::jm(Surv_object = surv21,
                         Mixed_objects = lme1, 
                         time_var = "time",
                         control = jmcontrol) 

summary(jmb2.121)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

### Dropping `alcohol 1-7/wk` variable

```{r}
table(swan_amh13.21$alcohol)
swan_amh13.22 <- swan_amh13.21
remove(swan_amh13.21)

surv22 <- coxph(Surv(etime, event) ~ 
                  0 + # alcohol +
                  bmi + # bc_pills + 
                  #children +
                  edu + 
                  # employed +
                  # health +
                  # married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.22, 
                x = TRUE,
                model = TRUE)

jmb2.122 <- JMbayes2::jm(Surv_object = surv22,
                         Mixed_objects = lme1, 
                         time_var = "time",
                         control = jmcontrol) 

summary(jmb2.122)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

### Dropping `edu Some College` variable

```{r}
table(swan_amh13.22$edu)
swan_amh13.23 <- swan_amh13.22
remove(swan_amh13.22)

surv23 <- coxph(Surv(etime, event) ~ 
                  0 + # alcohol +
                  bmi + # bc_pills + 
                  #children +
                  # edu + 
                  # employed +
                  # health +
                  # married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.23, 
                x = TRUE,
                model = TRUE)

jmb2.123 <- JMbayes2::jm(Surv_object = surv23,
                         Mixed_objects = lme1, 
                         time_var = "time",
                         control = jmcontrol) 

summary(jmb2.123)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable()
```

## Comparison

```{r}
#| label: "compare_models"
compare_jm(jmb2.111, 
           jmb2.112,
           jmb2.113, 
           jmb2.114,
           jmb2.115,
           jmb2.116,
           jmb2.117,
           jmb2.118,
           jmb2.119,
           jmb2.120,
           jmb2.121,
           jmb2.122,
           jmb2.123)
```

Need to discuss with EJC:

how to merge `alcohol` and `edu` levels.

`children` variable also need to be changed.

## Final model

```         
surv20 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + 
                  edu + 
                  married + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13.20, 
                x = TRUE,
                model = TRUE)

jmb2.120 <- JMbayes2::jm(Surv_object = surv20,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 
```

-   [x] `r praise::praise()`
