---
title: "Model Selection II - Factor"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warnings = FALSE,
                      message = FALSE,
                      comment = "#>",
                      cache = TRUE,
                      #results = "hide",
                      digits = 4,
                      error = FALSE)

# ## clean the R environment
# graphics.off()
# rm(list = ls())
# freshr::freshr()

## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(plyr)
library(JMbayes2, quietly = TRUE)
devtools::load_all()

## check the directory for the file
# here::dr_here()
here::set_here()

```

```{css, "css-setup", echo=FALSE}
.scroll-100 {
  max-height: 300px;
  max-width: 1000px;
  overflow-y: auto;
  background-color: inherit;
}
```

## Goal of the analysis

-   [x] Backward model selection joint model (without rate) with `JMbayes2`

-   [x] Rate model, Baseline Rate model, Value model comparison

-   [x] Tables for the models

-   [x] `r praise::praise()`

## Dummy variables for `site` and `ethnicity`

```{r}
#| label: "dummy_variables"

load("data/swan_amh03.rda")
load("data/swan_amh13.rda")


control = lmeControl(opt = "optim")
jmcontrol <- list(n_iter = 5000, 
                  n_burnin = 1000, 
                  n_chains = 3,
                  seed = 55555,
                  cores = 3)

lme1 <- lme(lamh ~ time,
                data = swan_amh03,
                control = control,
                random = ~ time| id)
```

## Fit the joint model

Need to keep $site + ethnic + smoke + bmi$

### Full model

```{r}

s10 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + bc_pills + 
                  children + edu + employed +
                  health +
                  married + 
                  phys_act + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13, 
                x = TRUE,
                model = TRUE)

jmb110 <- JMbayes2::jm(Surv_object = s10,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb110)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable(digits = 4)

```

### Dropping `health` variable

```{r}
## surv11 is the full model with all the variables
s11 <- coxph(Surv(etime, event) ~ 
                  0 + alcohol +
                  bmi + bc_pills + 
                  children + edu + employed +
                  # health +
                  married + 
                  phys_act + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13, 
                x = TRUE,
                model = TRUE)

jmb111 <- JMbayes2::jm(Surv_object = s11,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb111)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable(digits = 4)
```

```{r}
compare_jm(jmb110, jmb111)
```

### Dropping `alcohol` variable

```{r}
s12 <- coxph(Surv(etime, event) ~ 
                  0 + # alcohol +
                  bmi + 
                  bc_pills + 
                  children + 
                  edu +
                  employed +
                  # health +
                  married + 
                  phys_act + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13, 
                x = TRUE,
                model = TRUE)

jmb112 <- JMbayes2::jm(Surv_object = s12,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb112)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable(digits = 4)
```

```{r}
compare_jm(jmb111, jmb112)
```

### Dropping `bc_pills` variable

```{r}

s13 <- coxph(Surv(etime, event) ~ 
                  0 + # alcohol +
                  bmi + 
                  # bc_pills + 
                  children + 
                  edu + 
                  employed +
                  # health +
                  married + 
                  phys_act + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13, 
                x = TRUE,
                model = TRUE)

jmb113 <- JMbayes2::jm(Surv_object = s13,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb113)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable(digits = 4)
```

```{r}
compare_jm(jmb113, jmb112)
```

### **Dropping `education` variable**

```{r}

s14 <- coxph(Surv(etime, event) ~ 
                  0 + # alcohol +
                  bmi + 
                  # bc_pills + 
                  children + 
                  # edu + 
                  employed +
                  # health +
                  married + 
                  phys_act + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13, 
                x = TRUE,
                model = TRUE)

jmb114 <- JMbayes2::jm(Surv_object = s14,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb114)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable(digits = 4)

```

```{r}
compare_jm(jmb113, jmb114)
```

### Dropping `employed` variable

```{r}

s15 <- coxph(Surv(etime, event) ~ 
                  0 + # alcohol +
                  bmi + 
                  # bc_pills + 
                  children + 
                  # edu + 
                  # employed +
                  # health +
                  married + 
                  phys_act + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13, 
                x = TRUE,
                model = TRUE)

jmb115 <- JMbayes2::jm(Surv_object = s15,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb115)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable(digits = 4)
```

```{r}
compare_jm(jmb115, jmb114)
```

### Dropping `children` variable

```{r}

s16 <- coxph(Surv(etime, event) ~ 
                  0 + # alcohol +
                  bmi + 
                  # bc_pills + 
                  # children + 
                  # edu + 
                  # employed +
                  # health +
                  married + 
                  phys_act + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13, 
                x = TRUE,
                model = TRUE)

jmb116 <- JMbayes2::jm(Surv_object = s16,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb116)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable(digits = 4)
```

```{r}
compare_jm(jmb115, jmb116)
```

### Dropping `married` variable

```{r}

s17 <- coxph(Surv(etime, event) ~ 
                  0 + # alcohol +
                  bmi + 
                  # bc_pills + 
                  # children + 
                  # edu + 
                  # employed +
                  # health +
                  # married + 
                  phys_act + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13, 
                x = TRUE,
                model = TRUE)

jmb117 <- JMbayes2::jm(Surv_object = s17,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb117)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable(digits = 4)
```

```{r}
compare_jm(jmb116, jmb117)
```

### Dropping `phys_act` variable

```{r}

s18 <- coxph(Surv(etime, event) ~ 
                  0 + # alcohol +
                  bmi + 
                  # bc_pills + 
                  # children + 
                  # edu + 
                  # employed +
                  # health +
                  # married + 
                  # phys_act + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13, 
                x = TRUE,
                model = TRUE)

jmb118 <- JMbayes2::jm(Surv_object = s18,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 

summary(jmb118)$Survival %>% dplyr::arrange(desc(P)) %>% knitr::kable(digits = 4)
```

```{r}
compare_jm(jmb118, jmb117)
```

## Comparison for models

```{r}
compare_jm(jmb111, jmb112, jmb113, jmb114, jmb115, jmb116, jmb117, jmb118)
```

## The final model

For Chapter10, we have the model with `bc_pills` dropped from the new model.

$$
\begin{split}
  jmb117: & \\ 
  lme1: \ \ \  & \pmb m(time) = (fixed = lamh \sim time, \ random = \sim time| id) \\
  surv16: \ \ \ & Surv(etime, event) \sim phys_act + bmi + factor(site) + \\
  & factor(ethnic) + factor(smoke) + \pmb m(time)
\end{split}
$$

```         
s17 <- coxph(Surv(etime, event) ~ 
                  0 + # alcohol +
                  bmi + 
                  # bc_pills + 
                  # children + 
                  # edu + 
                  # employed +
                  # health +
                  # married + 
                  phys_act + 
                  ethnic_black + ethnic_chine + ethnic_hispa + ethnic_japan + 
                  site_c + site_m + site_nj + site_p + site_ucd + site_ucla + 
                  smoke_current_smoker + smoke_past_only,
                data = swan_amh13, 
                x = TRUE,
                model = TRUE)

jmb117 <- JMbayes2::jm(Surv_object = s17,
                               Mixed_objects = lme1, 
                               time_var = "time",
                               control = jmcontrol) 
```

-   [x] `r praise::praise()`
