---
title: "model 118"
author: "randy"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	error = FALSE,
	message = FALSE,
	comment = "#>",
	digits = 4,
	warnings = FALSE
)
## clean the R environment
graphics.off()
rm(list = ls())
freshr::freshr()

## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(gtsummary, quietly = TRUE)
library(flextable, quietly = TRUE)

## check the directory for the file
# here::dr_here()
here::set_here()

## the figure or results should be saved 
# paste0("foldername/Sfilename_workingresult_", 
#      Sys.Date(), ".filetype")
```

## FBMI

```{r}
load("results/118/jmbayes2_118_fbmi_value_rate_auc_only.RData")
tbl_auc_value_rate
```

```{r}
load("results/118/jmbayes2_118_fbmi_value_rate_auc_ci.RData")

AUC2_ci <- map_dfc(AUC2, "auc") %>% 
  map_dfr(~quantile(.x, c(0.5, 0.025, 0.975))) %>% 
  round(digit = 3) %>%
  unite(col = "95% CI", c("2.5%", "97.5%"), sep = " , ") %>%
  mutate(`95% CI` = paste0("(", `95% CI`, ")")) %>%
  unite(col = "AUC", c("50%", "95% CI"), sep = "  ") 

AUC3_ci <- map_dfc(AUC3, "auc") %>%
  map_dfr(~quantile(.x, c(0.5, 0.025, 0.975))) %>%
  round(digit = 3) %>%
  unite(col = "95% CI", c("2.5%", "97.5%"), sep = " , ") %>%
  mutate(`95% CI` = paste0("(", `95% CI`, ")")) %>%
  unite(col = "AUC", c("50%", "95% CI"), sep = "  ") 

AUC4_ci <- map_dfc(AUC4, "auc") %>%
  map_dfr(~quantile(.x, c(0.5, 0.025, 0.975))) %>%
  round(digit = 3) %>%
  unite(col = "95% CI", c("2.5%", "97.5%"), sep = " , ") %>%
  mutate(`95% CI` = paste0("(", `95% CI`, ")")) %>%
  unite(col = "AUC", c("50%", "95% CI"), sep = "  ") 

AUC5_ci <- map_dfc(AUC5, "auc") %>%
  map_dfr(~quantile(.x, c(0.5, 0.025, 0.975))) %>%
  round(digit = 3) %>%
  unite(col = "95% CI", c("2.5%", "97.5%"), sep = " , ") %>%
  mutate(`95% CI` = paste0("(", `95% CI`, ")")) %>%
  unite(col = "AUC", c("50%", "95% CI"), sep = "  ") 

AUC6_ci <- map_dfc(AUC6, "auc") %>%
  map_dfr(~quantile(.x, c(0.5, 0.025, 0.975))) %>%
  round(digit = 3) %>%
  unite(col = "95% CI", c("2.5%", "97.5%"), sep = " , ") %>%
  mutate(`95% CI` = paste0("(", `95% CI`, ")")) %>%
  unite(col = "AUC", c("50%", "95% CI"), sep = "  ") 

AUC8_ci <- map_dfc(AUC8, "auc") %>%
  map_dfr(~quantile(.x, c(0.5, 0.025, 0.975))) %>%
  round(digit = 3) %>%
  unite(col = "95% CI", c("2.5%", "97.5%"), sep = " , ") %>%
  mutate(`95% CI` = paste0("(", `95% CI`, ")")) %>%
  unite(col = "AUC", c("50%", "95% CI"), sep = "  ") 
```

```{r}
AUC2_ci <- rbind(NA, AUC2_ci)

AUC_final <- cbind(AUC2_ci, AUC3_ci,
                   AUC4_ci, AUC5_ci, 
                   AUC6_ci, AUC8_ci) 
colnames(AUC_final) <- c("Tstart2", "Tstart3", "Tstart4", "Tstart5", "Tstart6", "Tstart8")

AUC_final <- t(AUC_final)

colnames(AUC_final) <- c("Dt1", "Dt2", "Dt3", "Dt4", "Dt5")

```

For the final table each column is different `Dt` time window for predicting in $1, 2, 3, 4, 5$ years; each row is the `Tstart` time window for starting from the $2, 3, 4, 5, 6, 8$-th years. each cell is the AUC with 95% CI in the parenthesis `median (95% CI)`.

```{r}
AUC_final %>% 
  knitr::kable() %>%
  kableExtra::kable_styling(font_size = 8)

```

## AUC plot

```{r}
AUC2_ci <- map_dfc(AUC2, "auc") %>%
  map_dfr(~ quantile(.x, c(0.5, 0.025, 0.05, 0.1, 0.25, 0.75, 0.9, 0.95, 0.975))) %>%
  mutate(Tstart = 2)
AUC3_ci <- map_dfc(AUC3, "auc") %>%
  map_dfr(~ quantile(.x, c(0.5, 0.025, 0.05, 0.1, 0.25, 0.75, 0.9, 0.95, 0.975)))%>%
  mutate(Tstart = 3)
AUC4_ci <- map_dfc(AUC4, "auc") %>%
  map_dfr(~ quantile(.x, c(0.5, 0.025, 0.05, 0.1, 0.25, 0.75, 0.9, 0.95, 0.975)))%>%
  mutate(Tstart = 4)
AUC5_ci <- map_dfc(AUC5, "auc") %>%
  map_dfr(~ quantile(.x, c(0.5, 0.025, 0.05, 0.1, 0.25, 0.75, 0.9, 0.95, 0.975)))%>%
  mutate(Tstart = 5)
AUC6_ci <- map_dfc(AUC6, "auc") %>%
  map_dfr(~ quantile(.x, c(0.5, 0.025, 0.05, 0.1, 0.25, 0.75, 0.9, 0.95, 0.975)))%>%
  mutate(Tstart = 6)
AUC8_ci <- map_dfc(AUC8, "auc") %>%
  map_dfr(~ quantile(.x, c(0.5, 0.025, 0.05, 0.1, 0.25, 0.75, 0.9, 0.95, 0.975)))%>%
  mutate(Tstart = 8)

# AUC2_ci <- rbind(NA, AUC2_ci) %>%
#   mutate(Tstart = 2)

# View(AUC2_ci)

AUC_final <- rbind(AUC2_ci, AUC3_ci,
                   AUC4_ci, AUC5_ci, 
                   AUC6_ci, AUC8_ci) %>%
  mutate(Dt = c(2:5, rep(1:5, 5)))
```

### AUC and CI by Tstart

```{r}
#| fig.height: 6
#| fig.width: 9
## color codes for the palette
# Hex Codes: #355070 // #6d597a // #b56576 // #e56b6f // #eaac8b
# Hex Codes: #03045e // #0077b6 // #00b4d8 // #90e0ef // #caf0f8
# auc_plot <-
AUC_final %>%
  ggplot() +
  geom_line(aes(x = Dt, y = `2.5%`, group = Tstart),
              color = "#90e0ef", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Dt, y = `97.5%`, group = Tstart),
              color = "#90e0ef", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Dt, 
                    ymin = `2.5%`, 
                    ymax = `97.5%`,
                    group = Tstart),
                fill = "#90e0ef",
                alpha = 0.5) +
  geom_line(aes(x = Dt, y = `5%`, group = Tstart),
              color = "#00b4d8", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Dt, y = `95%`, group = Tstart),
              color = "#00b4d8", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Dt, 
                    ymin = `5%`, 
                    ymax = `95%`,
                    group = Tstart),
                fill = "#00b4d8",
                alpha = 0.5) +
    geom_line(aes(x = Dt, y = `10%`, group = Tstart),
              color = "#0077b6", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Dt, y = `90%`, group = Tstart),
              color = "#0077b6", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Dt, 
                    ymin = `10%`, 
                    ymax = `90%`,
                    group = Tstart),
                fill = "#0077b6",
                alpha = 0.5) +
    geom_line(aes(x = Dt, y = `25%`, group = Tstart),
              color = "#03045e", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Dt, y = `75%`, group = Tstart),
              color = "#03045e", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Dt, 
                    ymin = `25%`, 
                    ymax = `75%`,
                    group = Tstart),
                fill = "#03045e",
                alpha = 0.5) +
  geom_line(aes(x = Dt, y = `50%`, group = Tstart),
              color = "#fdc500", 
              linewidth = 0.5) +
  facet_wrap(~Tstart,
             labeller = labeller(
               Tstart = c("2" = "Starting Time 2nd year",
                          "3" = "Starting Time 3rd year",
                          "4" = "Starting Time 4th year",
                          "5" = "Starting Time 5th year",
                          "6" = "Starting Time 6th year",
                          "8" = "Starting Time 8th year"))) +
  labs(title = "SWAN-AMH AUC and CIs (wrap by starting time)") +
  theme_minimal() +
  xlab("Length of Time Interval (years)") +
  ylab("AUC") +
  theme(legend.position = "none",
        # panel.grid = element_blank(),
        # plot.margin = margin(t = 20, b = 8),
        # axis.text = element_blank(),
        # axis.title = element_blank(),
        strip.text = element_text(hjust = 0.5,
                                  lineheight = 0.1))
```

### AUC and CI by Dt

```{r}
#| fig.height: 6
#| fig.width: 6
# Hex Codes: #355070 // #6d597a // #b56576 // #e56b6f // #eaac8b
# Hex Codes: #03045e // #0077b6 // #00b4d8 // #90e0ef // #caf0f8
# auc_plot <-
AUC_final %>%
  filter(Dt != 1) %>%
  ggplot() +
  geom_line(aes(x = Tstart, y = `2.5%`, group = Dt),
              color = "#90e0ef", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Tstart, y = `97.5%`, group = Dt),
              color = "#90e0ef", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Tstart, 
                    ymin = `2.5%`, 
                    ymax = `97.5%`,
                    group = Dt),
                fill = "#90e0ef",
                alpha = 0.5) +
  geom_line(aes(x = Tstart, y = `5%`, group = Dt),
              color = "#00b4d8", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Tstart, y = `95%`, group = Dt),
              color = "#00b4d8", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Tstart, 
                    ymin = `5%`, 
                    ymax = `95%`,
                    group = Dt),
                fill = "#00b4d8",
                alpha = 0.5) +
    geom_line(aes(x = Tstart, y = `10%`, group = Dt),
              color = "#0077b6", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Tstart, y = `90%`, group = Dt),
              color = "#0077b6", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Tstart, 
                    ymin = `10%`, 
                    ymax = `90%`,
                    group = Dt),
                fill = "#0077b6",
                alpha = 0.5) +
    geom_line(aes(x = Tstart, y = `25%`, group = Dt),
              color =  "#03045e", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Tstart, y = `75%`, group = Dt),
              color = "#03045e", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Tstart, 
                    ymin = `25%`, 
                    ymax = `75%`,
                    group = Dt),
                fill = "#03045e",
                alpha = 0.5) +
  geom_line(aes(x = Tstart, y = `50%`, group = Dt),
              color = "#ffd500", 
              linewidth = 0.5) +
  facet_wrap(~Dt,
             labeller = labeller(
               Dt = c("1" = "1-year Time Interval",
                      "2" = "2-year Time Interval",
                      "3" = "3-year Time Interval",
                      "4" = "4-year Time Interval",
                      "5" = "5-year Time Interval"))) +
  labs(title = "SWAN-AMH AUC and CIs (wrap by time interval)") +
  theme_minimal() +
  xlab("Starting Time (year)") +
  ylab("AUC") +
  theme(legend.position = "none",
        # panel.grid = element_blank(),
        # plot.margin = margin(t = 20, b = 8),
        # axis.text = element_blank(),
        # axis.title = element_blank(),
        strip.text = element_text(hjust = 0.5,
                                  lineheight = 0.1))
```

## CBMI

```{r}
load("results/118/jmbayes2_118_cbmi_value_rate_auc_only.RData")
tbl_auc_value_rate
```

```{r}
load("results/118/jmbayes2_118_cbmi_value_rate_auc_ci.RData")

AUC2_ci <- map_dfc(AUC2, "auc") %>% 
  map_dfr(~quantile(.x, c(0.5, 0.025, 0.975))) %>% 
  round(digit = 3) %>%
  unite(col = "95% CI", c("2.5%", "97.5%"), sep = " , ") %>%
  mutate(`95% CI` = paste0("(", `95% CI`, ")")) %>%
  unite(col = "AUC", c("50%", "95% CI"), sep = "  ") 

AUC3_ci <- map_dfc(AUC3, "auc") %>%
  map_dfr(~quantile(.x, c(0.5, 0.025, 0.975))) %>%
  round(digit = 3) %>%
  unite(col = "95% CI", c("2.5%", "97.5%"), sep = " , ") %>%
  mutate(`95% CI` = paste0("(", `95% CI`, ")")) %>%
  unite(col = "AUC", c("50%", "95% CI"), sep = "  ") 

AUC4_ci <- map_dfc(AUC4, "auc") %>%
  map_dfr(~quantile(.x, c(0.5, 0.025, 0.975))) %>%
  round(digit = 3) %>%
  unite(col = "95% CI", c("2.5%", "97.5%"), sep = " , ") %>%
  mutate(`95% CI` = paste0("(", `95% CI`, ")")) %>%
  unite(col = "AUC", c("50%", "95% CI"), sep = "  ") 

AUC5_ci <- map_dfc(AUC5, "auc") %>%
  map_dfr(~quantile(.x, c(0.5, 0.025, 0.975))) %>%
  round(digit = 3) %>%
  unite(col = "95% CI", c("2.5%", "97.5%"), sep = " , ") %>%
  mutate(`95% CI` = paste0("(", `95% CI`, ")")) %>%
  unite(col = "AUC", c("50%", "95% CI"), sep = "  ") 

AUC6_ci <- map_dfc(AUC6, "auc") %>%
  map_dfr(~quantile(.x, c(0.5, 0.025, 0.975))) %>%
  round(digit = 3) %>%
  unite(col = "95% CI", c("2.5%", "97.5%"), sep = " , ") %>%
  mutate(`95% CI` = paste0("(", `95% CI`, ")")) %>%
  unite(col = "AUC", c("50%", "95% CI"), sep = "  ") 

AUC8_ci <- map_dfc(AUC8, "auc") %>%
  map_dfr(~quantile(.x, c(0.5, 0.025, 0.975))) %>%
  round(digit = 3) %>%
  unite(col = "95% CI", c("2.5%", "97.5%"), sep = " , ") %>%
  mutate(`95% CI` = paste0("(", `95% CI`, ")")) %>%
  unite(col = "AUC", c("50%", "95% CI"), sep = "  ") 
```

```{r}
AUC2_ci <- rbind(NA, AUC2_ci)

AUC_final <- cbind(AUC2_ci, AUC3_ci,
                   AUC4_ci, AUC5_ci, 
                   AUC6_ci, AUC8_ci) 
colnames(AUC_final) <- c("Tstart2", "Tstart3", "Tstart4", "Tstart5", "Tstart6", "Tstart8")

AUC_final <- t(AUC_final)

colnames(AUC_final) <- c("Dt1", "Dt2", "Dt3", "Dt4", "Dt5")

```

For the final table each column is different `Dt` time window for predicting in $1, 2, 3, 4, 5$ years; each row is the `Tstart` time window for starting from the $2, 3, 4, 5, 6, 8$-th years. each cell is the AUC with 95% CI in the parenthesis `median (95% CI)`.

```{r}
AUC_final %>% 
  knitr::kable() %>%
  kableExtra::kable_styling(font_size = 8)

```

## AUC plot

```{r}
AUC2_ci <- map_dfc(AUC2, "auc") %>%
  map_dfr(~ quantile(.x, c(0.5, 0.025, 0.05, 0.1, 0.25, 0.75, 0.9, 0.95, 0.975))) %>%
  mutate(Tstart = 2)
AUC3_ci <- map_dfc(AUC3, "auc") %>%
  map_dfr(~ quantile(.x, c(0.5, 0.025, 0.05, 0.1, 0.25, 0.75, 0.9, 0.95, 0.975)))%>%
  mutate(Tstart = 3)
AUC4_ci <- map_dfc(AUC4, "auc") %>%
  map_dfr(~ quantile(.x, c(0.5, 0.025, 0.05, 0.1, 0.25, 0.75, 0.9, 0.95, 0.975)))%>%
  mutate(Tstart = 4)
AUC5_ci <- map_dfc(AUC5, "auc") %>%
  map_dfr(~ quantile(.x, c(0.5, 0.025, 0.05, 0.1, 0.25, 0.75, 0.9, 0.95, 0.975)))%>%
  mutate(Tstart = 5)
AUC6_ci <- map_dfc(AUC6, "auc") %>%
  map_dfr(~ quantile(.x, c(0.5, 0.025, 0.05, 0.1, 0.25, 0.75, 0.9, 0.95, 0.975)))%>%
  mutate(Tstart = 6)
AUC8_ci <- map_dfc(AUC8, "auc") %>%
  map_dfr(~ quantile(.x, c(0.5, 0.025, 0.05, 0.1, 0.25, 0.75, 0.9, 0.95, 0.975)))%>%
  mutate(Tstart = 8)

# AUC2_ci <- rbind(NA, AUC2_ci) %>%
#   mutate(Tstart = 2)

# View(AUC2_ci)

AUC_final <- rbind(AUC2_ci, AUC3_ci,
                   AUC4_ci, AUC5_ci, 
                   AUC6_ci, AUC8_ci) %>%
  mutate(Dt = c(2:5, rep(1:5, 5)))
```

### AUC and CI by Tstart

```{r}
#| fig.height: 6
#| fig.width: 9
## color codes for the palette
# Hex Codes: #355070 // #6d597a // #b56576 // #e56b6f // #eaac8b
# Hex Codes: #03045e // #0077b6 // #00b4d8 // #90e0ef // #caf0f8
# auc_plot <-
AUC_final %>%
  ggplot() +
  geom_line(aes(x = Dt, y = `2.5%`, group = Tstart),
              color = "#90e0ef", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Dt, y = `97.5%`, group = Tstart),
              color = "#90e0ef", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Dt, 
                    ymin = `2.5%`, 
                    ymax = `97.5%`,
                    group = Tstart),
                fill = "#90e0ef",
                alpha = 0.5) +
  geom_line(aes(x = Dt, y = `5%`, group = Tstart),
              color = "#00b4d8", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Dt, y = `95%`, group = Tstart),
              color = "#00b4d8", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Dt, 
                    ymin = `5%`, 
                    ymax = `95%`,
                    group = Tstart),
                fill = "#00b4d8",
                alpha = 0.5) +
    geom_line(aes(x = Dt, y = `10%`, group = Tstart),
              color = "#0077b6", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Dt, y = `90%`, group = Tstart),
              color = "#0077b6", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Dt, 
                    ymin = `10%`, 
                    ymax = `90%`,
                    group = Tstart),
                fill = "#0077b6",
                alpha = 0.5) +
    geom_line(aes(x = Dt, y = `25%`, group = Tstart),
              color = "#03045e", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Dt, y = `75%`, group = Tstart),
              color = "#03045e", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Dt, 
                    ymin = `25%`, 
                    ymax = `75%`,
                    group = Tstart),
                fill = "#03045e",
                alpha = 0.5) +
  geom_line(aes(x = Dt, y = `50%`, group = Tstart),
              color = "#fdc500", 
              linewidth = 0.5) +
  facet_wrap(~Tstart,
             labeller = labeller(
               Tstart = c("2" = "Starting Time 2nd year",
                          "3" = "Starting Time 3rd year",
                          "4" = "Starting Time 4th year",
                          "5" = "Starting Time 5th year",
                          "6" = "Starting Time 6th year",
                          "8" = "Starting Time 8th year"))) +
  labs(title = "SWAN-AMH AUC and CIs (wrap by starting time)") +
  theme_minimal() +
  xlab("Length of Time Interval (years)") +
  ylab("AUC") +
  theme(legend.position = "none",
        # panel.grid = element_blank(),
        # plot.margin = margin(t = 20, b = 8),
        # axis.text = element_blank(),
        # axis.title = element_blank(),
        strip.text = element_text(hjust = 0.5,
                                  lineheight = 0.1))
```

### AUC and CI by Dt

```{r}
#| fig.height: 6
#| fig.width: 6
# Hex Codes: #355070 // #6d597a // #b56576 // #e56b6f // #eaac8b
# Hex Codes: #03045e // #0077b6 // #00b4d8 // #90e0ef // #caf0f8
# auc_plot <-
AUC_final %>%
  filter(Dt != 1) %>%
  ggplot() +
  geom_line(aes(x = Tstart, y = `2.5%`, group = Dt),
              color = "#90e0ef", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Tstart, y = `97.5%`, group = Dt),
              color = "#90e0ef", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Tstart, 
                    ymin = `2.5%`, 
                    ymax = `97.5%`,
                    group = Dt),
                fill = "#90e0ef",
                alpha = 0.5) +
  geom_line(aes(x = Tstart, y = `5%`, group = Dt),
              color = "#00b4d8", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Tstart, y = `95%`, group = Dt),
              color = "#00b4d8", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Tstart, 
                    ymin = `5%`, 
                    ymax = `95%`,
                    group = Dt),
                fill = "#00b4d8",
                alpha = 0.5) +
    geom_line(aes(x = Tstart, y = `10%`, group = Dt),
              color = "#0077b6", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Tstart, y = `90%`, group = Dt),
              color = "#0077b6", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Tstart, 
                    ymin = `10%`, 
                    ymax = `90%`,
                    group = Dt),
                fill = "#0077b6",
                alpha = 0.5) +
    geom_line(aes(x = Tstart, y = `25%`, group = Dt),
              color =  "#03045e", linetype = "dashed",
              alpha = 0.5) +
    geom_line(aes(x = Tstart, y = `75%`, group = Dt),
              color = "#03045e", linetype = "dashed",
              alpha = 0.5) +
    geom_ribbon(aes(x = Tstart, 
                    ymin = `25%`, 
                    ymax = `75%`,
                    group = Dt),
                fill = "#03045e",
                alpha = 0.5) +
  geom_line(aes(x = Tstart, y = `50%`, group = Dt),
              color = "#ffd500", 
              linewidth = 0.5) +
  facet_wrap(~Dt,
             labeller = labeller(
               Dt = c("1" = "1-year Time Interval",
                      "2" = "2-year Time Interval",
                      "3" = "3-year Time Interval",
                      "4" = "4-year Time Interval",
                      "5" = "5-year Time Interval"))) +
  labs(title = "SWAN-AMH AUC and CIs (wrap by time interval)") +
  theme_minimal() +
  xlab("Starting Time (year)") +
  ylab("AUC") +
  theme(legend.position = "none",
        # panel.grid = element_blank(),
        # plot.margin = margin(t = 20, b = 8),
        # axis.text = element_blank(),
        # axis.title = element_blank(),
        strip.text = element_text(hjust = 0.5,
                                  lineheight = 0.1))
```
