---
title: "Life table"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warnings = FALSE,
                      message = FALSE,
                      comment = "#>",
                      #results = "hide",
                      digits = 4,
                      error = FALSE)

## clean the R environment
# graphics.off()
# rm(list = ls())
# freshr::freshr()

## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(gtsummary, quietly = TRUE)
library(flextable, quietly = TRUE)
library(survival, quietly = TRUE)
library(knitr, quietly = TRUE)
library(kableExtra, quietly = TRUE)

## check the directory for the file
# here::dr_here()
here::set_here()

## the figure or results should be saved 
# paste0("foldername/Sfilename_workingresult_", 
#      Sys.Date(), ".filetype")
```

```{css, echo=FALSE}
.scroll-100 {
  max-height: 300px;
  max-width: 1000px;
  overflow-y: auto;
  background-color: inherit;
}
```

## Goal for this chapter

-   [x] Life table for both training and testing datasets

-   [x] the number of events in each stratified time intervals

-   [x] the number of observation in each stratified time intervals

    -   [x] personally this is also need to see the proportion of events in each stratified time intervals

## The Contingency Table for events only

Here are the tables for the events only Training and Testing datasets.

### Training

```{r}
swan_amh1 <- read_csv("data-raw/swan_amh1.csv")

## pullout the life tbl for the test_amh1
sfit <- survfit(Surv(etime, event) ~ 1, data = swan_amh1)

## aggregate the life table by every year
## the number of events in each stratified time 
## intervals

ltbl <- function(step) {
  periods <- seq(0, 22, step)
  
  data <- data.frame(sfit$time, sfit$n.event, sfit$n.risk) %>%
    rbind(c(3, 0, max(sfit$n.risk)+min(sfit$n.risk)),
          c(2, 0, max(sfit$n.risk)+min(sfit$n.risk)),
          c(1, 0, max(sfit$n.risk)+min(sfit$n.risk)),
          c(0, 0, max(sfit$n.risk)+min(sfit$n.risk))) %>%
    arrange(sfit.time)
  
  tbl <- data %>%
    mutate(groups = cut(as.numeric(data$sfit.time), 
                        breaks = periods, 
                        labels = periods[-1])) %>%
    group_by(groups) %>%
    summarise(n.event = sum(sfit.n.event),
              n.risk = max(sfit.n.risk)) %>%
    mutate(Tstart = as.numeric(as.character(groups)) - step,
           Tend = as.numeric(as.character(groups))) %>%
    dplyr::select(Tstart, Tend, Events = n.event, AtRisks = n.risk) %>%
    filter(!is.na(Tstart))

  return(tbl)
}

tbl_train <- map(list(1, 2, 3, 4, 5), ltbl)
knitr::kable(tbl_train[1])
knitr::kable(tbl_train[2])
knitr::kable(tbl_train[3])
knitr::kable(tbl_train[4])
knitr::kable(tbl_train[5])
```

### Testing

```{r}
test_amh1 <- read_csv("data-raw/test_amh1.csv") %>% 
  mutate(event = 1)

## pullout the life tbl for the test_amh1
sfit <- survfit(Surv(etime, event) ~ 1, data = test_amh1)

tbl_tests <-  map(list(1, 2, 3, 4, 5), ltbl)
 
knitr::kable(tbl_tests[1])
knitr::kable(tbl_tests[2])
knitr::kable(tbl_tests[3])
knitr::kable(tbl_tests[4])
knitr::kable(tbl_tests[5])
```
