---
title: "Final Report"
author: "randy"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: yes
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      eval = TRUE,
                      warnings = FALSE,
                      message = FALSE,
                      comment = "#>",
                      cache = TRUE,
                      #results = "hide",
                      digits = 4,
                      error = FALSE)

## clean the R environment
# graphics.off()
# rm(list = ls())
# freshr::freshr()

## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(gtsummary, quietly = TRUE)
library(flextable, quietly = TRUE)
library(JMbayes2)
devtools::load_all()

## check the directory for the file
# here::dr_here()
here::set_here()

## the figure or results should be saved 
# paste0("foldername/Sfilename_workingresult_", 
#      Sys.Date(), ".filetype")
```

\newpage

## Goal of the analysis

-   [x] Fit the final joint model with rate with `JMbayes2` based on model selection results

-   [x] Table1

-   [x] Life Tables for Training and Testing datasets

-   [x] Dynamic prediction for the joint model

-   [x] Training dataset

    -   [x] Calculate the AUC for the joint model for $Dt = 1, 2, 3, 4, 5$ (year)

    -   [x] Calculate the Brier score for the joint model for $Dt = 1, 2, 3, 4, 5$ (year)

-   [x] Testing dataset

    -   [x] Calculate the AUC for the joint model for $Dt = 1, 2, 3, 4, 5$ (year)

    -   [x] Calculate the Brier score for the joint model for $Dt = 1, 2, 3, 4, 5$ (year)

\newpage

## Final Table1

```{r}

swan_amh0 <- read_csv("data-raw/swan_amh0.csv") %>%
  mutate(alcohol = factor(alcohol,
                          levels = c(0, 1, 2, 3),
                          labels = c("None","<1/wk", "1-7/wk", ">7/wk")),
        
        edu = factor(edu,
                      levels = c(1, 2, 3),
                      labels = c("High School or Less",
                                 "Some College",
                                 "College degree or higher")),
        employed = factor(employed,
                           levels = c(0, 1),
                           labels = c("Unemployed",
                                      "Employed")),
        health = factor(health,
                         levels = c(1, 2, 3, 4),
                         labels = c("Excellent",
                                    "Very Good",
                                    "Good",
                                    "Fair/Poor")),
        meno = factor(meno,
                      levels = c(0, 1, 2, 3),
                      labels = c('Pre', 'Early Peri', 'Late Peri', 'Post')),
        smoke = factor(smoke,
                        levels = c(1, 2, 3),
                        labels = c("Never Smoked",
                                   "Past Only",
                                   "Current Smoker")),
        married = factor(married,
                          levels = c(0,1),
                          labels = c("Not Married/Partnered",
                                     "Married/Partnered")),
        bc_pills = factor(bc_pills,
                           levels = c(0, 1),
                           labels = c("Never",
                                      "Ever use BC pills")),
        bmi_cat = case_when(bmi < 25 ~ 1,
                             bmi >= 25 & bmi < 30 ~ 2,
                             bmi >= 30 ~ 3),
         bmi_cat = as.factor(bmi_cat))
  

all_amh0 <- test_amh0 %>% 
  filter(!is.na(amh)) %>%
  mutate(id = as.integer(id),
         lamh = log(amh)) %>%
  rbind(swan_amh0) %>% 
  mutate(group = factor(train, levels = c(1, 0),
                        labels = c("0Training", "1Testing"))) %>% 
  filter(!is.na(time))

all_amh1 <- all_amh0 %>%
  group_by(id) %>%
  summarize(# tn = max(time),
            # t0 = min(time),
            # dt = tn - t0,
            visitn = n()) 

all_amh2 <- all_amh0 %>%
  dplyr::select(id, age, ethnic, married,
                alcohol, smoke, bc_pills,
                bmi, health, phys_act, amh,
                meno, 
                # parity, children,
                group,
                etime,
                employed, edu, site)  %>%
  mutate(site = case_when(site == "11" ~ "M",
                          site == "12" ~ "B",
                          site =="13" ~ "C",
                          site =="14" ~ "UCD",
                          site =="15" ~ "UCLA",
                          site =="16" ~ "NJ",
                          site =="17" ~ "P")) %>%
  group_by(id) %>%
  slice(1L) %>%
  ungroup() %>%
  full_join(all_amh1, by = "id")


table1_final <- all_amh2 %>%
  mutate(visitn = as.numeric(visitn)) %>% 
  ungroup() %>%
  dplyr::select(-id) %>%
  tbl_summary(by = group,
              missing = "ifany",
              label = list(c("age") ~ "Baseline Age (years)",
                           c("ethnic") ~ "Ethnicity / Race",
                           c("married") ~ "Marital Status",
                           c("alcohol") ~ "Alcohol Use",
                           c("smoke") ~ "Smoking History",
                           c("bc_pills") ~ "Ever use of BC Pills",
                           c("bmi") ~ "BMI",
                           c("health") ~ "Overall Health",
                           c("phys_act") ~ "Physical Activity Score",
                           c("amh") ~ "Baseline AMH",
                           c("etime") ~ "Event Time",
                           c("meno") ~ "Menopausal Status",
                           # c("parity") ~ "Parity",
                           # c("children") ~ "Children",
                           c("employed") ~ "Employment Status",
                           c("edu") ~ "Educational Attainment",
                           c("site") ~ "Study Site",
                           c("visitn") ~ "Visiting Numbers"),
              type = list(all_continuous() ~ "continuous2",
                          "visitn" ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                                    "{median}",
                                                    "[{min}, {max}]"),
                               all_categorical() ~ "{n} / {N} ({p}%)")) %>%
  modify_header(label = "**Characteristics**") %>%
  # update the column header
  bold_labels() %>%
  add_overall() %>%
  italicize_labels()
```

For testing dataset there are missings for `amh` and the visit numbers are different from the training.

```{r}
table1_final
```

## Contingency Table

### Training

```{r}
swan_amh1 <- read_csv("data-raw/swan_amh1.csv")

## pullout the life tbl for the test_amh1
sfit <- survfit(Surv(etime, event) ~ 1, data = swan_amh1)

## aggregate the life table by every year
## the number of events in each stratified time 
## intervals

ltbl <- function(step) {
  periods <- seq(0, 22, step)
  
  data <- data.frame(sfit$time, sfit$n.event, sfit$n.risk) %>%
    rbind(c(3, 0, max(sfit$n.risk) + min(sfit$n.risk)),
          c(2, 0, max(sfit$n.risk) + min(sfit$n.risk)),
          c(1, 0, max(sfit$n.risk) + min(sfit$n.risk)),
          c(0, 0, max(sfit$n.risk) + min(sfit$n.risk))) %>%
    arrange(sfit.time)
  
  tbl <- data %>%
    mutate(groups = cut(as.numeric(data$sfit.time), 
                        breaks = periods, 
                        labels = periods[-1])) %>%
    group_by(groups) %>%
    summarise(n.event = sum(sfit.n.event),
              n.risk = max(sfit.n.risk)) %>%
    mutate(Tstart = as.numeric(as.character(groups)) - step,
           Tend = as.numeric(as.character(groups))) %>%
    dplyr::select(Tstart, Tend, Events = n.event, AtRisks = n.risk) %>%
    filter(!is.na(Tstart))

  return(tbl)
}

tbl_train <- map(list(1, 2, 3, 4, 5), ltbl)
```

### 1 Year Interval

```{r}
knitr::kable(tbl_train[1])
```

### 2 Year Interval

```{r}
knitr::kable(tbl_train[2])
```

### 3 Year Interval

```{r}
knitr::kable(tbl_train[3])
```

### 4 Year Interval

```{r}
knitr::kable(tbl_train[4])
```

### 5 Year Interval

```{r}
knitr::kable(tbl_train[5])
```

\newpage

### Testing

```{r}
test_amh1 <- read_csv("data-raw/test_amh1.csv") %>% 
  mutate(event = 1)

## pullout the life tbl for the test_amh1
sfit <- survfit(Surv(etime, event) ~ 1, data = test_amh1)

tbl_tests <-  map(list(1, 2, 3, 4, 5), ltbl)

```

### 1 Year Interval

```{r}
knitr::kable(tbl_tests[1])
```

### 2 Year Interval

```{r}
knitr::kable(tbl_tests[2])
```

### 3 Year Interval

```{r}
knitr::kable(tbl_tests[3])
```

### 4 Year Interval

```{r}
knitr::kable(tbl_tests[4])
```

### 5 Year Interval

```{r}
knitr::kable(tbl_tests[5])
```

\newpage

## Final Model

### Value + Rate model

$$
\begin{split}
  jmb2.119.value.rate: & \\ 
  lme1: \ \ \  & \pmb m(time) = (fixed = lamh \sim time,\\
  & \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  \ \ \ \ \ \  random = time| id) \\
  surv19: \ \ \ & Surv(etime, event) \sim  factor(bmi) + site + ethnic + smoke \\
  & \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ + \pmb m(time) + \pmb m'(time) 
\end{split}
$$

Fitting the model with:

-   Chain 5
-   Iteration 500k
-   Thinning 50
-   Total iterations of 50k

\newpage

### Summarization

```{r}
load("results/jmb2_119_chain5_it500k_thin50_total50k.Rdata")

summary(jmb2.119.value.rate)
```

\newpage

### SD Calculation for slope term

```{r}
random_intercept <- cbind(jmb2.119.value.rate$mcmc$b[[1]][, 1, ]) 
                          # jmb2.119.value.rate$mcmc$b[[2]][, 1, ], 
                          # jmb2.119.value.rate$mcmc$b[[3]][, 1, ], 
                          # jmb2.119.value.rate$mcmc$b[[4]][, 1, ])
fixed_intercept <- cbind(t(jmb2.119.value.rate$mcmc$betas1[[1]][, 1]))
                         # t(jmb2.119.value.rate$mcmc$betas1[[2]][, 1]), 
                         # t(jmb2.119.value.rate$mcmc$betas1[[3]][, 1]), 
                         # t(jmb2.119.value.rate$mcmc$betas1[[4]][, 1]))

# random_intercept <- random[, 1, ] 

random_slope <- cbind(jmb2.119.value.rate$mcmc$b[[1]][, 2, ])
                      # jmb2.119.value.rate$mcmc$b[[2]][, 2, ], 
                      # jmb2.119.value.rate$mcmc$b[[3]][, 2, ], 
                      # jmb2.119.value.rate$mcmc$b[[4]][, 2, ])
fixed_slope <- cbind(t(jmb2.119.value.rate$mcmc$betas1[[1]][, 2]))
                     # t(jmb2.119.value.rate$mcmc$betas1[[2]][, 2]), 
                     # t(jmb2.119.value.rate$mcmc$betas1[[3]][, 2]), 
                     # t(jmb2.119.value.rate$mcmc$betas1[[4]][, 2]))

# View(fixed_slope)
# dim(random_slope)
# dim(fixed_slope)

both_intercept <- random_intercept + as.vector(fixed_intercept)
both_slope <- random_slope + as.vector(fixed_slope)

# dim(both_slope)
# dim(both_intercept)
```

```{r}
both_int_sd <- apply(both_intercept, 1, sd)
both_slope_sd <- apply(both_slope, 1, sd)

both_int_mu <- apply(both_intercept, 1, mean)
both_slope_mu <- apply(both_slope, 1, mean)

# cat("The mean of mu(both_int)", 
#     mean(both_int_mu), ";\n")
# 
# cat("The mean of SD(both_int)", 
#     mean(both_int_sd), 
#     ";\n the median of SD(both_int)",
#     median(both_int_sd), "\n")
# 
# 
# cat("The mean of mu(both_slope)",
#     mean(both_slope_mu), ";\n")
# 
# cat("The mean of SD(both_slope)",
#     mean(both_slope_sd), 
#     ";\n the median of SD(both_slope)",
#     median(both_slope_sd), "\n")
# 
# quantile(both_slope, c(0.025,0.5, 0.975))
# 
# mean(both_slope_mu) - 1.96 * mean(both_slope_sd)
# mean(both_slope_mu) + 1.96 * mean(both_slope_sd)
```

```{r}
random_int_sd <- apply(random_intercept, 1, sd)
random_slope_sd <- apply(random_slope, 1, sd)

random_int_mu <- apply(random_intercept, 1, mean)
random_slope_mu <- apply(random_slope, 1, mean)

# cat("The mean of mu(random_int)", 
#     mean(random_int_mu), ";\n")
# 
# cat("The mean of mu(random_slope)",
#     mean(random_slope_mu), ";\n")
# 
# 
# cat("The mean of SD(random_int)", 
#     mean(random_int_sd), 
#     ";\n the median of SD(random_int)",
#     median(random_int_sd), "\n")
# 
# cat("The mean of SD(random_slope)",
#     mean(random_slope_sd), 
#     ";\n the median of SD(random_slope)",
#     median(random_slope_sd), "\n")

```

Hence, we have the final results for the variability of the slope term.

-   The mean value for both slopes : `r random_slope` + `r as.vector(fixed_slope)` = `r both_slope`;

-   The random effect slope term based on MCMC is $\sigma_{\beta_1}$ = `r mean(random_slope_sd)`;

-   The fixed effect slope term $\sigma_{b_1}$ = `r summary(jmb2.119.value.rate)$Outcome[2, 2]`;

-   We have the pooled $\sigma_{b1 + \beta1}$ = `r sqrt(summary(jmb2.119.value.rate)$Outcome[2, 2]^2 + mean(random_slope_sd)^2)`.

-   The 95% CI for the slope term is (`r summary(jmb2.119.value.rate)$Outcome[2, 1]- 1.96 * sqrt(summary(jmb2.119.value.rate)$Outcome[2, 2]^2 + mean(random_slope_sd)^2)`, `r summary(jmb2.119.value.rate)$Outcome[2, 1] + 1.96 * sqrt(summary(jmb2.119.value.rate)$Outcome[2, 2]^2 + mean(random_slope_sd)^2)`)

\newpage

## Prediction Performance

### Training set

#### AUC

```{r}
load("results/jmb2_119_auc_chain5_it500k_thin100_total25k.Rdata")

tbl_auc_value_rate %>% knitr::kable()
```

#### Brier Scores

```{r}
load("results/jmb2_119_brier_chain5_it500k_thin100_total25k.Rdata")

tbl_bs_value_rate %>% knitr::kable()
```

\newpage

### Testing set

#### AUC

```{r}
load("results/jmb2_119_test_auc_chain5_it500k_thin50_total50k.Rdata")

tbl_auc_value_rate_test %>% knitr::kable()
```

#### Brier Scores

```{r}
load("results/jmb2_119_test_brier_chain5_it500k_thin50_total50k.Rdata")

tbl_bs_value_rate_test %>% knitr::kable()
```
