---
title: "24_checking"
date: "2024-09-26"
output:
  pdf_document:
    toc: true
    toc_depth: '2'
  word_document:
    toc: true
    toc_depth: 2
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warnings = FALSE,
                      message = FALSE,
                      comment = "#>",
                      cache = TRUE,
                      #results = "hide",
                      digits = 4,
                      error = FALSE)

## clean the R environment
graphics.off()
rm(list = ls())
freshr::freshr()

## load packages
library(here, quietly = TRUE)
library(tidyverse, quietly = TRUE)
library(JMbayes2, quietly = TRUE)
library(survival, quietly = TRUE)
library(knitr, quietly = TRUE)
library(kableExtra, quietly = TRUE)

## check the directory for the file
# here::dr_here()
# here::set_here()
```

## Kaplan-Meire Curve

```{r message=FALSE, warning=FALSE, include=FALSE}
swan_amh1 <- read_csv("data-raw/swan_amh1.csv") %>%
  mutate(meno = as.character(meno))
test_amh1 <- read_csv("data-raw/test_amh1.csv") %>% 
  mutate(event = 1)
all_amh1 <- bind_rows(swan_amh1, test_amh1) %>%
  mutate(train = ifelse(train == 0, "testing", "training"),
         train = as.factor(train))

## pullout the life tbl for the test_amh1
```

```{r message=FALSE, warning=FALSE}
km.plot <- function(var, 
                    vard) {
  vard <- as.factor(vard)
  surv1 <- paste("Surv(start_time, etime, event) ~", 
                 var, sep = " ")
  sfit <- survfit(formula(surv1),
                  data = all_amh1)
  lev <- levels(vard)
  str(vard)
  nlev <- nlevels(vard)
  plot(sfit, 
       lty = 1:nlev,
       lwd = 2, 
       col = 1:nlev,
       main = var)
  legend("topright", lev, 
         lty = 1:nlev, 
         col = 1:nlev, 
         lwd = 2,
         bty = "n")
}

km.plot(var = "train", vard = all_amh1$train)

```

```{r message=FALSE, warning=FALSE}
load("data/test_amh0.rda")
test_amh01 <- test_amh0 %>%
  mutate(site = case_when(site == "11" ~ "M",
                          site == "12" ~ "B",
                          site =="13" ~ "C",
                          site =="14" ~ "UCD",
                          site =="15" ~ "UCLA",
                          site =="16" ~ "NJ",
                          site =="17" ~ "P"),
         lamh = log(amh),
         ethnic = factor(ethnic, levels = c("CAUCA", "BLACK",
                                            "CHINE", "HISPA",
                                            "JAPAN")),
         bmi_cat = as.factor(bmi_cat),
         # site = factor(site, levels = c("B", "C", "M",
         #                                "NJ", "P",
         #                                "UCD", "UCLA")),
         smoke = factor(smoke, levels = c("Never Smoked" ,
                                          "Past Only",
                                          "Current Smoker"))) %>% 
  cbind(model.matrix(~ 1 + site + ethnic + smoke,
                     data = .)) %>%
  janitor::clean_names() %>%
  dplyr::select(-intercept) %>%
  dplyr::select(order(colnames(.))) %>% 
  filter(!is.na(time))

load("data/swan_amh03.rda")
swan_amh04 <- swan_amh03 %>%
  group_by(id) %>%
  arrange(time) %>%
  slice(1L) %>%
  dplyr::select(id, lamh0 = lamh) %>%
  mutate(id = as.character(id))

swan_amh03 <- swan_amh03 %>%
  mutate(id = as.character(id)) %>%
  full_join(swan_amh04, by = "id") %>%
  mutate(bmi_cat = case_when(bmi < 25 ~ 1,
                             bmi >= 25 & bmi < 30 ~ 2,
                             bmi >= 30 ~ 3),
         bmi_cat = as.factor(bmi_cat))
```

## Longitudinal Spaghetti Plot 

```{r fig.height=4, fig.width=5, message=TRUE, warning=FALSE}
load("results/margin_data_longitudinal_mean.Rdata")

plot3 <- ggplot() +
  geom_line(data = test_amh01,
            aes(x = time, y = lamh, group = id),
            color = "#8B3A3A", alpha = 0.1) +
  geom_line(data = swan_amh03, 
            aes(x = time, y = lamh, group = id),
            color = "#27408B", alpha = 0.1) +
  geom_line(data = margin_data,
            aes(x = time, y = lamh),
            size = 1,
            color = "#fdc500") 
plot3 + ylim(c(0, 7)) +
  xlim(c(0, 16)) +
  # labs(title = "SWAN-AMH AUC and CIs (wrap by time interval)") +
  theme_bw() +
  xlab("Time (year)") +
  ylab("log(AMH)") +
  theme(legend.position = "none",
        # panel.grid = element_blank(),
        # plot.margin = margin(t = 20, b = 8),
        # axis.text = element_blank(),
        # axis.title = element_blank(),
        strip.text = element_text(hjust = 0.5,
                                  lineheight = 0.1))
```

## Age and Other Distribution

```{r message=FALSE, warning=FALSE}
train03 <- swan_amh03 %>% 
  ungroup() %>%
  filter(!is.na(amh)) %>% 
  group_by(id) %>%
  dplyr::summarize(visit = n()) %>%
  as.data.frame()

test03 <- test_amh01 %>% 
  filter(!is.na(amh)) %>% 
  ungroup() %>%
  group_by(id) %>%
  dplyr::summarize(visit = n()) %>%
  as.data.frame() %>%
  mutate(visit = as.numeric(visit))

plot2 <- ggplot() +
  geom_histogram(data = train03, aes(x = visit), 
                 fill = "blue", 
                 stat = "count",
                 binwidth = 1,
                 alpha = 0.5) +
  geom_histogram(data = test03, aes(x = visit),
                 fill = "red", 
                 stat = "count",
                 binwidth = 1,
                 alpha = 0.5) +
  labs(title = "Histogram of the number of visits",
       x = "Number of visits",
       y = "Frequency") +
  theme_minimal()
plot2
```

```{r message=FALSE, warning=FALSE}
train03 <- swan_amh03 %>% 
  ungroup() %>%
  # filter(!is.na(amh)) %>% 
  group_by(id) %>%
  dplyr::summarize(visit = n()) %>%
  as.data.frame()

test03 <- test_amh01 %>% 
  # filter(!is.na(amh)) %>% 
  ungroup() %>%
  group_by(id) %>%
  dplyr::summarize(visit = n()) %>%
  as.data.frame() %>%
  mutate(visit = as.numeric(visit))

plot1 <- ggplot() +
  geom_histogram(data = train03, aes(x = visit), 
                 fill = "blue", 
                 stat = "count",
                 binwidth = 1,
                 alpha = 0.5) +
  geom_histogram(data = test03, aes(x = visit),
                 fill = "red", 
                 stat = "count",
                 binwidth = 1,
                 alpha = 0.5) +
  labs(title = "Histogram of the number of visits",
       x = "Number of visits",
       y = "Frequency") +
  theme_minimal()
plot1

```

```{r message=FALSE, warning=FALSE}
load("data/swan_amh03.rda")
load("data/swan_amh13.rda")

swan_amh04 <- swan_amh03 %>%
  group_by(id) %>%
  arrange(time) %>%
  slice(1L) %>%
  dplyr::select(id, lamh0 = lamh) %>%
  mutate(id = as.character(id))

swan_amh03 <- swan_amh03 %>%
  mutate(id = as.character(id)) %>%
  full_join(swan_amh04, by = "id") %>%
  mutate(bmi_cat = case_when(bmi < 25 ~ 1,
                             bmi >= 25 & bmi < 30 ~ 2,
                             bmi >= 30 ~ 3),
         bmi_cat = as.factor(bmi_cat)) %>%
  filter(!is.na(amh))

swan_amh13 <- swan_amh13 %>%
  full_join(swan_amh04, by = "id") %>%
  mutate(bmi_cat = case_when(bmi < 25 ~ 1,
                             bmi >= 25 & bmi < 30 ~ 2,
                             bmi >= 30 ~ 3),
         bmi_cat = as.factor(bmi_cat))

load("data/test_amh0.rda")
load("data/test_amh1.rda")

test_amh01 <- test_amh0 %>%
  mutate(site = case_when(site == "11" ~ "M",
                          site == "12" ~ "B",
                          site =="13" ~ "C",
                          site =="14" ~ "UCD",
                          site =="15" ~ "UCLA",
                          site =="16" ~ "NJ",
                          site =="17" ~ "P"),
         lamh = log(amh),
         ethnic = factor(ethnic, levels = c("CAUCA", "BLACK",
                                            "CHINE", "HISPA",
                                            "JAPAN")),
         bmi_cat = as.factor(bmi_cat),
         # site = factor(site, levels = c("B", "C", "M",
         #                                "NJ", "P",
         #                                "UCD", "UCLA")),
         smoke = factor(smoke, levels = c("Never Smoked" ,
                                          "Past Only",
                                          "Current Smoker"))) %>% 
  cbind(model.matrix(~ 1 + site + ethnic + smoke,
                     data = .)) %>%
  janitor::clean_names() %>%
  dplyr::select(-intercept) %>%
  dplyr::select(order(colnames(.))) %>% 
  filter(!is.na(time), 
         !is.na(amh))

summary_test <- test_amh01 %>%
  group_by(id) %>%
  dplyr::summarize(visit = n(),
                   etime = as.integer(mean(etime)), 
                   age_min = as.integer(min(age)),
                   age_max = as.integer(max(age)),
                   age_gap = age_max - age_min) %>%
  as.data.frame()

summary_train <- swan_amh03 %>%
  group_by(id) %>%
  dplyr::summarize(visit = n(),
                   etime = as.integer(mean(etime)),
                   age_min = as.integer(min(age)),
                   age_max = as.integer(max(age)),
                   age_gap = age_max - age_min) %>%
  as.data.frame()

plot01 <- ggplot() +
  geom_histogram(data = summary_train, aes(x = age_min), 
                 fill = "blue", 
                 stat = "count",
                 binwidth = 1,
                 alpha = 0.5) +
  geom_histogram(data = summary_test, aes(x = age_min),
                 fill = "red", 
                 stat = "count",
                 binwidth = 1,
                 alpha = 0.5) +
  labs(title = "Histogram of Starting age",
       x = "Age",
       y = "Frequency") +
  theme_minimal()
plot02 <- ggplot() +
  geom_histogram(data = summary_train, aes(x = age_max), 
                 fill = "blue", 
                 stat = "count",
                 binwidth = 1,
                 alpha = 0.5) +
  geom_histogram(data = summary_test, aes(x = age_max),
                 fill = "red", 
                 stat = "count",
                 binwidth = 1,
                 alpha = 0.5) +
  labs(title = "Histogram of Ending age",
       x = "Age",
       y = "Frequency") +
  theme_minimal()
plot03 <- ggplot() +
  geom_histogram(data = summary_train, aes(x = age_gap), 
                 fill = "blue", 
                 stat = "count",
                 binwidth = 1,
                 alpha = 0.5) +
  geom_histogram(data = summary_test, aes(x = age_gap),
                 fill = "red", 
                 stat = "count",
                 binwidth = 1,
                 alpha = 0.5) +
  labs(title = "Histogram of Gap of time",
       x = "Time",
       y = "Frequency") +
  theme_minimal()
plot04 <- ggplot() +
  geom_histogram(data = summary_train, aes(x = etime), 
                 fill = "blue", 
                 binwidth = 1,
                 alpha = 0.5,) +
  geom_histogram(data = summary_test, aes(x = etime),
                 fill = "red", 
                 binwidth = 1,
                 alpha = 0.5) +
  labs(title = "Histogram of Event time",
       x = "Time",
       y = "Frequency") +
  theme_minimal()
plot01; plot02; plot03; plot04

```

```{r}
#| warning: false
#| message: false
plot11 <- ggplot() +
  geom_histogram(data = summary_train, aes(x = age_min, y = ..density..), 
                 fill = "blue", 
                 stat = "density",
                 binwidth = 1,
                 alpha = 0.5) +
  geom_histogram(data = summary_test, aes(x = age_min, y = ..density..),
                 fill = "red", 
                 stat = "density",
                 binwidth = 1,
                 alpha = 0.5) +
  labs(title = "Density of Starting age",
       x = "Age",
       y = "Frequency") +
  theme_minimal()
plot12 <- ggplot() +
  geom_histogram(data = summary_train, aes(x = age_max, y = ..density..), 
                 fill = "blue", 
                 stat = "density",
                 binwidth = 1,
                 alpha = 0.5) +
  geom_histogram(data = summary_test, aes(x = age_max, y = ..density..),
                 fill = "red", 
                 stat = "density",
                 binwidth = 1,
                 alpha = 0.5) +
  labs(title = "Density of Ending age",
       x = "Age",
       y = "Frequency") +
  theme_minimal()
plot13 <- ggplot() +
  geom_histogram(data = summary_train, aes(x = age_gap, y = ..density..), 
                 fill = "blue", 
                 stat = "density",
                 binwidth = 1,
                 alpha = 0.5) +
  geom_histogram(data = summary_test, aes(x = age_gap, y = ..density..),
                 fill = "red", 
                 stat = "density",
                 binwidth = 1,
                 alpha = 0.5) +
  labs(title = "Density of Gap of time",
       x = "Time",
       y = "Frequency") +
  theme_minimal()
plot14 <- ggplot() +
  geom_histogram(data = summary_train, aes(x = etime, y = ..density..), 
                 fill = "blue", 
                 binwidth = 1,
                 stat = "density",
                 alpha = 0.5,) +
  geom_histogram(data = summary_test, aes(x = etime, y = ..density..),
                 fill = "red", 
                 binwidth = 1,
                 stat = "density",
                 alpha = 0.5) +
  labs(title = "Density of Event time",
       x = "Time",
       y = "Frequency") +
  theme_minimal()
plot11; plot12; plot13; plot14
```

## AUC Rerun

### Training AUC

```{r}
load("results/jmb2_119_auc_train_chain_10_it200k_thin100_total20k.Rdata")
tbl_auc_value_rate %>% knitr::kable()
```

### Testing AUC

```{r}
load("results/jmb2_119_auc_test_chain_10_it200k_thin100_total20k.Rdata")
tbl_auc_value_rate_test %>% knitr::kable()
```

## Brier Score Rerun


```{r}
load("~/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/amh/results/jmb2_119_test_brier_chain10_it200k_thin100_total20k.Rdata")


load("~/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/amh/results/jmb2_119_train_brier_chain10_it200k_thin100_total20k.Rdata")
```

### Training Brier Score

```{r}
tbl_bs_value_rate %>% knitr::kable()
```

### Testing Brier Score

```{r}
tbl_bs_value_rate_test %>% knitr::kable()
```


## Joint model random intercept SD

```{r}
load("results/jmb2_119_chain10_it200k_thin100_total20k.Rdata")
summary <- summary(jmb2.119.value.rate)
random_intercept <- cbind(jmb2.119.value.rate$mcmc$b[[1]][, 1, ],
                          jmb2.119.value.rate$mcmc$b[[2]][, 1, ],
                          jmb2.119.value.rate$mcmc$b[[3]][, 1, ],
                          jmb2.119.value.rate$mcmc$b[[4]][, 1, ],
                          jmb2.119.value.rate$mcmc$b[[5]][, 1, ])
fixed_intercept <- cbind(t(jmb2.119.value.rate$mcmc$betas1[[1]][, 1]),
                         t(jmb2.119.value.rate$mcmc$betas1[[2]][, 1]),
                         t(jmb2.119.value.rate$mcmc$betas1[[3]][, 1]),
                         t(jmb2.119.value.rate$mcmc$betas1[[4]][, 1]),
                         t(jmb2.119.value.rate$mcmc$betas1[[5]][, 1]))

# random_intercept <- random[, 1, ] 

random_slope <- cbind(jmb2.119.value.rate$mcmc$b[[1]][, 2, ],
                      jmb2.119.value.rate$mcmc$b[[2]][, 2, ],
                      jmb2.119.value.rate$mcmc$b[[3]][, 2, ],
                      jmb2.119.value.rate$mcmc$b[[4]][, 2, ],
                      jmb2.119.value.rate$mcmc$b[[5]][, 2, ])
fixed_slope <- cbind(t(jmb2.119.value.rate$mcmc$betas1[[1]][, 2]),
                     t(jmb2.119.value.rate$mcmc$betas1[[2]][, 2]),
                     t(jmb2.119.value.rate$mcmc$betas1[[3]][, 2]),
                     t(jmb2.119.value.rate$mcmc$betas1[[4]][, 2]),
                     t(jmb2.119.value.rate$mcmc$betas1[[5]][, 2]))
remove(jmb2.119.value.rate)

both_intercept <- random_intercept + as.vector(fixed_intercept)
both_slope <- random_slope + as.vector(fixed_slope)
```

```{r}
both_int_sd <- apply(both_intercept, 1, sd)
both_slope_sd <- apply(both_slope, 1, sd)

both_int_mu <- apply(both_intercept, 1, mean)
both_slope_mu <- apply(both_slope, 1, mean)
```

```{r}
random_intercept_sd <- apply(random_intercept, 1, sd)
random_slope_sd <- apply(random_slope, 1, sd)

random_int_mu <- apply(random_intercept, 1, mean)
random_slope_mu <- apply(random_slope, 1, mean)

```

Hence, we have the final results for the variability of the intercept term.

-   The mean value for both intercept : `r mean(random_intercept)` + `r mean(as.vector(fixed_intercept))` = `r mean(both_intercept)`;

-   The random effect intercept term based on MCMC is $\sigma_{\beta_0}$ = `r mean(random_intercept_sd)`;

-   The fixed effect intercept term $\sigma_{b_0}$ = `r summary$Outcome[1, 2]`;

-   We have the pooled $\sigma_{b0 + \beta0}$ = `r sqrt(summary$Outcome[1, 2]^2 + mean(random_intercept_sd)^2)`.

-   The 95% CI for the intercept term is (`r summary$Outcome[1, 1]- 1.96 * sqrt(summary$Outcome[1, 2]^2 + mean(random_intercept_sd)^2)`, `r summary$Outcome[1, 1] + 1.96 * sqrt(summary$Outcome[1, 2]^2 + mean(random_intercept_sd)^2)`)
